---
title: "Loops_analysis_single_and_merged_replicates"
---

### SINGLE_REPLICATES ###

# [ChIA-PET single replicates] Upload the loops 
```{r}
experiment="chiapet"
cell_lines=c("GM19238_rep1", "GM19238_rep2", "GM19239_rep1", "GM19239_rep2","GM19240_rep1","GM19240_rep2")
trios=c("GM19238", "GM19239", "GM19240")

# Read loops files - all
loops_single_chiapet_all=vector(mode="list", length=NROW(cell_lines))
names(loops_single_chiapet_all)=cell_lines
for (cell_line in cell_lines){
  loops_single_chiapet_all[[cell_line]]=read.table(
    list.files(paste0("data/", experiment, "/", cell_line), pattern='\\.e500.clusters.cis.BE3$', recursive=FALSE, full.names = TRUE))
  colnames(loops_single_chiapet_all[[cell_line]])=c("anch_1","start_1","end_1","anch_2","start_2","end_2","pets_count")
}

# Read loops files - all
loops_single_chiapet_2_anchors=vector(mode="list", length=NROW(cell_lines))
names(loops_single_chiapet_2_anchors)=cell_lines
for (cell_line in cell_lines){
  loops_single_chiapet_2_anchors[[cell_line]]=read.table(
    list.files(paste0("data/", experiment, "/", cell_line), pattern='.e500.clusters.cis.BE3.peak_annot.E2', recursive=FALSE, full.names = TRUE))
  colnames(loops_single_chiapet_2_anchors[[cell_line]])=c("anch_1","start_1","end_1","anch_2","start_2","end_2","pets_count")
}
```

# [HiChIP single replicates] Upload the loops 
```{r}
experiment="hichip"
cell_lines=c("GM19238_rep1", "GM19238_rep2", "GM19239_rep1", "GM19239_rep2","GM19240_rep1","GM19240_rep2")
trios=c("GM19238", "GM19239", "GM19240")

# Read loops files - all
loops_single_hichip_all=vector(mode="list", length=NROW(cell_lines))
names(loops_single_hichip_all)=cell_lines
for (cell_line in cell_lines){
  loops_single_hichip_all[[cell_line]]=read.table(
    list.files(paste0("data/", experiment, "/", cell_line), pattern='\\.e500.clusters.cis.BE3$', recursive=FALSE, full.names = TRUE))
  colnames(loops_single_hichip_all[[cell_line]])=c("anch_1","start_1","end_1","anch_2","start_2","end_2","pets_count")
}

# Read loops files - all
loops_single_hichip_2_anchors=vector(mode="list", length=NROW(cell_lines))
names(loops_single_hichip_2_anchors)=cell_lines
for (cell_line in cell_lines){
  loops_single_hichip_2_anchors[[cell_line]]=read.table(
    list.files(paste0("data/", experiment, "/", cell_line), pattern='.e500.clusters.cis.BE3.peak_annot.E2', recursive=FALSE, full.names = TRUE))
  colnames(loops_single_hichip_2_anchors[[cell_line]])=c("anch_1","start_1","end_1","anch_2","start_2","end_2","pets_count")
}
```

# [ChIA-PET single replicates] Compare the all loops quantity
```{r}

experiment="chiapet"

# Generate the comulative distribution plot

png(paste0('plots/loops/Comulative_distribution_plot_', experiment, '_all_loops_single_replicates_GM19239_tr.png'), res = 300, width = 1500, height = 1900)

plot.new()
i=n=1
# for (cell_line in cell_lines){
for (cell_line in cell_lines[c(3,4)]){
  ecdf_plot=plot(
    ecdf(loops_single_chiapet_all[[cell_line]]$pets_count),
    cex=0.8,
    # xlim=c(3,max(loops_single_chiapet_all[[cell_line]]$pets_count)),
    xlim=c(3,50),
    # col=color(trios[i]),
    col=color(cell_line),
    ylim=c(0.2,1), add=ifelse(n==1, FALSE, TRUE),
    xlab="PETs count",
    ylab="Cumulative percent",
    # pch=19)
    pch=ifelse(!is.na(str_extract(cell_line, "rep1")),19, 0),
    main=prop_name(experiment))
  # grid()
  abline(h=c(0.2,0.4,0.5,0.6,0.7,0.8,0.9), 
         v=c(5,10,15,20,30,40,50),col="grey", lty=3, )
  abline(h=1, lty=2)
  n=n+1
  if(n==3 | n==5){i=i+1}}
legend("bottomright", 
       title="Cell Line",
       # legend=cell_lines,
       legend=cell_lines[c(3,4)],
       pch=c(19,0,19,0,19,0,19),
       col=c(color(cell_lines[3]), color(cell_lines[4])))
       # col=c(color(trios[1]), color(trios[1]), color(trios[2]), color(trios[2]), color(trios[3]), color(trios[3])))
dev.off()

# See the cumulative numbers
# ecdf(loops_single_chiapet_all[[cell_line]]$pets_count)(sort(loops_single_chiapet_all[[cell_line]]$pets_count))

# Calculate the average PETs number of 99% of replicates and mean in the sample
chiapet_cum_percent_loops_single=vector(mode="list", length=NROW(loops_single_chiapet_all))
names(chiapet_cum_percent_loops_single)=cell_lines
for (cell_line in cell_lines){
  chiapet_cum_percent_loops_single[[cell_line]]=
    c(quantile(loops_single_chiapet_all[[cell_line]]$pets_count, probs=seq(0,1,0.99)),
  mean(loops_single_chiapet_all[[cell_line]]$pets_count))
  names(chiapet_cum_percent_loops_single[[cell_line]])[3]="mean"
}

```

# [HiChIP single replicates] Compare the all loops quantity
```{r}

experiment="hichip"

# Generate the comulative distribution plot

png(paste0('plots/loops/Comulative_distribution_plot_', experiment, '_all_loops_single_replicates.png'), res = 300, width = 1500, height = 1500)

plot.new()
i=n=1
for (cell_line in cell_lines){
  ecdf_plot=plot(ecdf(loops_single_hichip_all[[cell_line]]$pets_count),
     cex=0.5,
     # xlim=c(3,max(loops_single_hichip_all[[cell_line]]$pets_count)),
     xlim=c(3,50),
     col=color(trios[i]),
     ylim=c(0.2,1), add=ifelse(n==1, FALSE, TRUE),
     xlab="PETs count",
     ylab="Cumulative percent",
     # pch=19)
     pch=ifelse(!is.na(str_extract(cell_line, "rep1")),0, 19),
     main="")
  n=n+1
  if(n==3 | n==5){i=i+1}}
legend("bottomright", 
       title="Cell Line",
       legend=cell_lines,
       pch=c(0,19,0,19,0,19),
       col=c(color(trios[1]), color(trios[1]), color(trios[2]), color(trios[2]), color(trios[3]), color(trios[3])))
dev.off()

# GM19239
# Generate the comulative distribution plot

png(paste0('plots/loops/Comulative_distribution_plot_', experiment, '_GM19239_tr.png'), res = 300, width = 1500, height = 1900)

plot.new()
i=n=1
for (cell_line in cell_lines[c(3,4)]){
  ecdf_plot=plot(
    ecdf(loops_single_hichip_all[[cell_line]]$pets_count),
    cex=0.8,
    xlim=c(3,50),
    col=color(cell_line),
    ylim=c(0.2,1), add=ifelse(n==1, FALSE, TRUE),
    xlab="PETs count",
    ylab="Cumulative percent",
    pch=ifelse(!is.na(str_extract(cell_line, "rep1")),19, 0),
    main="Hi-ChIP")
  abline(h=c(0.2,0.4,0.5,0.6,0.7,0.8,0.9), 
         v=c(5,10,15,20,30,40,50),col="grey", lty=3, )
  abline(h=1, lty=2)
  n=n+1
  if(n==3 | n==5){i=i+1}}
legend("bottomright", 
       title="Cell Line",
       legend=cell_lines[c(3,4)],
       pch=c(19,0),
       col=c(color(cell_lines[3]), color(cell_lines[4])))
dev.off()

# See the cumulative numbers
# ecdf(loops_single_hichip_all[[cell_line]]$pets_count)(sort(loops_single_hichip_all[[cell_line]]$pets_count))

# Calculate the average PETs number of 99% of replicates and mean in the sample
hichip_cum_percent_loops_single=vector(mode="list", length=NROW(loops_single_hichip_all))
names(hichip_cum_percent_loops_single)=cell_lines
for (cell_line in cell_lines){
  hichip_cum_percent_loops_single[[cell_line]]=
    c(quantile(loops_single_hichip_all[[cell_line]]$pets_count, probs=seq(0,1,0.99)),
  mean(loops_single_hichip_all[[cell_line]]$pets_count))
  names(hichip_cum_percent_loops_single[[cell_line]])[3]="mean"
}

```

# [ChIA-PET single replicates] Compare the loops with 2 anchors quantity
```{r}
experiment="chiapet"

# Generate the comulative distribution plot

png(paste0('plots/loops/Comulative_distribution_plot_', experiment, '_2_anchors_single_replicates.png'), res = 300, width = 1500, height = 1500)

plot.new()
i=n=1
for (cell_line in cell_lines){
  ecdf_plot=plot(ecdf(loops_single_chiapet_2_anchors[[cell_line]]$pets_count),
     cex=0.5,
     # xlim=c(3,max(loops_single_chiapet_2_anchors[[cell_line]]$pets_count)),
     xlim=c(3,50),
     col=color(trios[i]),
     ylim=c(0.2,1), add=ifelse(n==1, FALSE, TRUE),
     xlab="PETs count",
     ylab="Cumulative percent",
     # pch=19)
     pch=ifelse(!is.na(str_extract(cell_line, "rep1")),0, 19),
     main="",)
  n=n+1
  if(n==3 | n==5){i=i+1}}
legend("bottomright", 
       title="Cell Line",
       legend=cell_lines,
       pch=c(0,19,0,19,0,19),
       col=c(color(trios[1]), color(trios[1]), color(trios[2]), color(trios[2]), color(trios[3]), color(trios[3])))
dev.off()

png(paste0('plots/loops/Comulative_distribution_plot_', experiment, '_2_anchors_GM19239_tr.png'), res = 300, width = 1500, height = 1900)
#Gm19239
plot.new()
i=n=1
# for (cell_line in cell_lines){
for (cell_line in cell_lines[c(3,4)]){
  ecdf_plot=plot(
    ecdf(loops_single_chiapet_2_anchors[[cell_line]]$pets_count),
    cex=0.8,
    xlim=c(3,50),
    col=color(cell_line),
    ylim=c(0.2,1), add=ifelse(n==1, FALSE, TRUE),
    xlab="PETs count",
    ylab="Cumulative percent",
    pch=ifelse(!is.na(str_extract(cell_line, "rep1")),19, 0),
    main=prop_name(experiment))
  abline(h=c(0.2,0.4,0.5,0.6,0.7,0.8,0.9), 
         v=c(5,10,15,20,30,40,50),col="grey", lty=3, )
  abline(h=1, lty=2)
  n=n+1
  if(n==3 | n==5){i=i+1}}
legend("bottomright", 
       title="Cell Line",
       legend=cell_lines[c(3,4)],
       pch=c(19,0,19,0,19,0,19),
       col=c(color(cell_lines[3]), color(cell_lines[4])))
dev.off()


# Calculate the average PETs number of 99% of replicates and mean in the sample
chiapet_cum_percent_2anch_loops_single=vector(mode="list", length=NROW(loops_single_chiapet_2_anchors))
names(chiapet_cum_percent_2anch_loops_single)=cell_lines
for (cell_line in cell_lines){
  chiapet_cum_percent_2anch_loops_single[[cell_line]]=
    c(quantile(loops_single_chiapet_2_anchors[[cell_line]]$pets_count, probs=seq(0,1,0.99)),
  mean(loops_single_chiapet_2_anchors[[cell_line]]$pets_count))
  names(chiapet_cum_percent_2anch_loops_single[[cell_line]])[3]="mean"
}
```

# [HiChIP single replicates] Compare the loops with 2 anchors quantity
```{r}
experiment="hichip"

# Generate the comulative distribution plot

png(paste0('plots/loops/Comulative_distribution_plot_', experiment, '_2_anchors_single_replicates.png'), res = 300, width = 1500, height = 1500)

plot.new()
i=n=1
for (cell_line in cell_lines){
  ecdf_plot=plot(ecdf(loops_single_hichip_2_anchors[[cell_line]]$pets_count),
     cex=0.5,
     # xlim=c(3,max(loops_single_hichip_2_anchors[[cell_line]]$pets_count)),
     xlim=c(3,50),
     col=color(trios[i]),
     ylim=c(0.2,1), add=ifelse(n==1, FALSE, TRUE),
     xlab="PETs count",
     ylab="Cumulative percent",
     # pch=19)
     pch=ifelse(!is.na(str_extract(cell_line, "rep1")),0, 19),
     main="",)
  n=n+1
  if(n==3 | n==5){i=i+1}}
legend("bottomright", 
       title="Cell Line",
       legend=cell_lines,
       pch=c(0,19,0,19,0,19),
       col=c(color(trios[1]), color(trios[1]), color(trios[2]), color(trios[2]), color(trios[3]), color(trios[3])))
dev.off()

#GM19239
png(paste0('plots/loops/Comulative_distribution_plot_', experiment, '_2_anchors_GM19239_tr.png'), res = 300, width = 1500, height = 1900)

plot.new()
i=n=1
for (cell_line in cell_lines[c(3,4)]){
  ecdf_plot=plot(
    ecdf(loops_single_hichip_2_anchors[[cell_line]]$pets_count),
    cex=0.8,
    xlim=c(3,50),
    col=color(cell_line),
    ylim=c(0.2,1), add=ifelse(n==1, FALSE, TRUE),
    xlab="PETs count",
    ylab="Cumulative percent",
    pch=ifelse(!is.na(str_extract(cell_line, "rep1")),19, 0),
    main="Hi-ChIP")
  abline(h=c(0.2,0.4,0.5,0.6,0.7,0.8,0.9), 
         v=c(5,10,15,20,30,40,50),col="grey", lty=3, )
  abline(h=1, lty=2)
  n=n+1
  if(n==3 | n==5){i=i+1}}
legend("bottomright", 
       title="Cell Line",
       legend=cell_lines[c(3,4)],
       pch=c(19,0),
       col=c(color(cell_lines[3]), color(cell_lines[4])))
dev.off()

# Calculate the average PETs number of 99% of replicates and mean in the sample
hichip_cum_percent_2anch_loops_single=vector(mode="list", length=NROW(loops_single_hichip_2_anchors))
names(hichip_cum_percent_2anch_loops_single)=cell_lines
for (cell_line in cell_lines){
  hichip_cum_percent_2anch_loops_single[[cell_line]]=
    c(quantile(loops_single_hichip_2_anchors[[cell_line]]$pets_count, probs=seq(0,1,0.99)),
  mean(loops_single_hichip_2_anchors[[cell_line]]$pets_count))
  names(hichip_cum_percent_2anch_loops_single[[cell_line]])[3]="mean"
}
```


### MERGED_REPLICATES ###

# [ChIA-PET merged replicates] Upload the loops 
```{r}
experiment="chiapet"
trios=c("GM19238", "GM19239", "GM19240")

# Read loops files - all
loops_chiapet_all=vector(mode="list", length=NROW(trios))
names(loops_chiapet_all)=trios
for (cell_line in trios){
  loops_chiapet_all[[cell_line]]=read.table(
    list.files(paste0("data/", experiment, "/", cell_line), pattern='\\.e500.clusters.cis.BE3$', recursive=FALSE, full.names = TRUE))
  colnames(loops_chiapet_all[[cell_line]])=c("anch_1","start_1","end_1","anch_2","start_2","end_2","pets_count")
}

# Read loops files - all
loops_chiapet_2_anchors=vector(mode="list", length=NROW(trios))
names(loops_chiapet_2_anchors)=trios
for (cell_line in trios){
  loops_chiapet_2_anchors[[cell_line]]=read.table(
    list.files(paste0("data/", experiment, "/", cell_line), pattern='.e500.clusters.cis.BE3.peak_annot.E2$', recursive=FALSE, full.names = TRUE))
  colnames(loops_chiapet_2_anchors[[cell_line]])=c("anch_1","start_1","end_1","anch_2","start_2","end_2","pets_count")
}
```

# [HiChIP merged replicates] Upload the loops 
```{r}
experiment="hichip"
trios=c("GM19238", "GM19239", "GM19240")

# Read loops files - all
loops_hichip_all=vector(mode="list", length=NROW(trios))
names(loops_hichip_all)=trios
for (cell_line in trios){
  loops_hichip_all[[cell_line]]=read.table(
    list.files(paste0("data/", experiment, "/", cell_line), pattern='\\.e500.clusters.cis.BE3$', recursive=FALSE, full.names = TRUE))
  colnames(loops_hichip_all[[cell_line]])=c("anch_1","start_1","end_1","anch_2","start_2","end_2","pets_count")
}

# Read loops files - all
loops_hichip_2_anchors=vector(mode="list", length=NROW(trios))
names(loops_hichip_2_anchors)=trios
for (cell_line in trios){
  loops_hichip_2_anchors[[cell_line]]=read.table(
    list.files(paste0("data/", experiment, "/", cell_line), pattern='.e500.clusters.cis.BE3.peak_annot.E2$', recursive=FALSE, full.names = TRUE))
  colnames(loops_hichip_2_anchors[[cell_line]])=c("anch_1","start_1","end_1","anch_2","start_2","end_2","pets_count")
}
```

# [ChIA-PET merged replicates] Compare the all loops quantity
```{r}

experiment="chiapet"

# Generate the comulative distribution plot

png(paste0('plots/loops/Comulative_distribution_plot_', experiment, '_all_loops_merged_replicates.png'), res = 300, width = 1500, height = 1500)

plot.new()
i=n=1
for (cell_line in trios){
  ecdf_plot=plot(ecdf(loops_chiapet_all[[cell_line]]$pets_count),
     cex=0.5,
     # xlim=c(3,max(loops_chiapet_all[[cell_line]]$pets_count)),
     xlim=c(3,50),
     col=color(cell_line),
     ylim=c(0.2,1), add=ifelse(n==1, FALSE, TRUE),
     xlab="PETs count",
     ylab="Cumulative percent",
     # pch=19)
     pch=19,
     main="")
  n=n+1
  if(n==3 | n==5){i=i+1}}
legend("bottomright", 
       title="Cell Line",
       legend=trios,
       pch=c(19,19,19),
       col=c(color(trios[1]), color(trios[2]), color(trios[3])))
dev.off()

# Calculate the average PETs number of 99% of replicates and mean in the sample
chiapet_cum_percent_loops=vector(mode="list", length=NROW(loops_chiapet_all))
names(chiapet_cum_percent_loops)=trios
for (cell_line in trios){
  chiapet_cum_percent_loops[[cell_line]]=
    c(quantile(loops_chiapet_all[[cell_line]]$pets_count, probs=seq(0,1,0.99)),
  mean(loops_chiapet_all[[cell_line]]$pets_count))
  names(chiapet_cum_percent_loops[[cell_line]])[3]="mean"
}

```

# [HiChIP merged replicates] Compare the all loops quantity
```{r}

experiment="hichip"

# Generate the comulative distribution plot

png(paste0('plots/loops/Comulative_distribution_plot_', experiment, '_all_loops_merged_replicates.png'), res = 300, width = 1500, height = 1500)

plot.new()
i=n=1
for (cell_line in trios){
  ecdf_plot=plot(ecdf(loops_hichip_all[[cell_line]]$pets_count),
     cex=0.5,
     # xlim=c(3,max(loops_hichip_all[[cell_line]]$pets_count)),
     xlim=c(3,50),
     col=color(cell_line),
     ylim=c(0.2,1), add=ifelse(n==1, FALSE, TRUE),
     xlab="PETs count",
     ylab="Cumulative percent",
     # pch=19)
     pch=19,
     main="")
  n=n+1
  if(n==3 | n==5){i=i+1}}
legend("bottomright", 
       title="Cell Line",
       legend=trios,
       pch=c(19,19,19),
       col=c(color(trios[1]), color(trios[2]), color(trios[3])))
dev.off()

# See the cumulative numbers
ecdf(loops_hichip_all[[cell_line]]$pets_count)(sort(loops_hichip_all[[cell_line]]$pets_count))

# Calculate the average PETs number of 99% of replicates and mean in the sample
hichip_cum_percent_loops=vector(mode="list", length=NROW(loops_hichip_all))
names(hichip_cum_percent_loops)=trios
for (cell_line in trios){
  hichip_cum_percent_loops[[cell_line]]=
    c(quantile(loops_hichip_all[[cell_line]]$pets_count, probs=seq(0,1,0.99)),
  mean(loops_hichip_all[[cell_line]]$pets_count))
  names(hichip_cum_percent_loops[[cell_line]])[3]="mean"
}

```

# [ChIA-PET merged replicates] Compare the loops with 2 anchors quantity
```{r}
experiment="chiapet"

# Generate the comulative distribution plot

png(paste0('plots/loops/Comulative_distribution_plot_', experiment, '_2_anchors_merged_replicates.png'), res = 300, width = 1500, height = 1500)

plot.new()
i=n=1
for (cell_line in trios){
  ecdf_plot=plot(ecdf(loops_chiapet_2_anchors[[cell_line]]$pets_count),
     cex=0.5,
     # xlim=c(3,max(loops_chiapet_2_anchors[[cell_line]]$pets_count)),
     xlim=c(3,50),
     col=color(cell_line),
     ylim=c(0.2,1), add=ifelse(n==1, FALSE, TRUE),
     xlab="PETs count",
     ylab="Cumulative percent",
     # pch=19)
     pch=19,
     main="")
  n=n+1
  if(n==3 | n==5){i=i+1}}
legend("bottomright", 
       title="Cell Line",
       legend=trios,
       pch=c(19,19,19),
       col=c(color(trios[1]), color(trios[2]), color(trios[3])))
dev.off()

# Calculate the average PETs number of 99% of replicates and mean in the sample
chiapet_cum_percent_2anch_loops=vector(mode="list", length=NROW(loops_chiapet_2_anchors))
names(chiapet_cum_percent_2anch_loops)=trios
for (cell_line in trios){
  chiapet_cum_percent_2anch_loops[[cell_line]]=
    c(quantile(loops_chiapet_2_anchors[[cell_line]]$pets_count, probs=seq(0,1,0.99)),
  mean(loops_chiapet_2_anchors[[cell_line]]$pets_count))
  names(chiapet_cum_percent_2anch_loops[[cell_line]])[3]="mean"
}
```

# [HiChIP merged replicates] Compare the loops with 2 anchors quantity
```{r}
experiment="hichip"

# Generate the comulative distribution plot

png(paste0('plots/loops/Comulative_distribution_plot_', experiment, '_2_anchors_merged_replicates.png'), res = 300, width = 1500, height = 1500)

plot.new()
i=n=1
for (cell_line in trios){
  ecdf_plot=plot(ecdf(loops_hichip_2_anchors[[cell_line]]$pets_count),
     cex=0.5,
     # xlim=c(3,max(loops_hichip_all[[cell_line]]$pets_count)),
     xlim=c(3,50),
     col=color(cell_line),
     ylim=c(0.2,1), add=ifelse(n==1, FALSE, TRUE),
     xlab="PETs count",
     ylab="Cumulative percent",
     # pch=19)
     pch=19,
     main="")
  n=n+1
  if(n==3 | n==5){i=i+1}}
legend("bottomright", 
       title="Cell Line",
       legend=trios,
       pch=c(19,19,19),
       col=c(color(trios[1]), color(trios[2]), color(trios[3])))
dev.off()

# Calculate the average PETs number of 99% of replicates and mean in the sample
hichip_cum_percent_2anch_loops=vector(mode="list", length=NROW(loops_hichip_2_anchors))
names(hichip_cum_percent_2anch_loops)=trios
for (cell_line in trios){
  hichip_cum_percent_2anch_loops[[cell_line]]=
    c(quantile(loops_hichip_2_anchors[[cell_line]]$pets_count, probs=seq(0,1,0.99)),
  mean(loops_hichip_2_anchors[[cell_line]]$pets_count))
  names(hichip_cum_percent_2anch_loops[[cell_line]])[3]="mean"
}
```

# Apply the cleaning filter on the merged loops
```{r}
# Loops ChIA-PET
loops_chiapet_GM19238_clean=clean_all_loops(read.table("data/chiapet/GM19238/GM19238_merged_replicates.e500.clusters.cis.BE3"),
                                            read.table("data/chiapet/GM19238/GM19238_merged_replicates.for.BROWSER.spp.z6.broadPeak"),
                                            3, CTCF.hg38)

loops_chiapet_GM19239_clean=clean_all_loops(read.table("data/chiapet/GM19239/GM19239_merged_replicates.e500.clusters.cis.BE3"),
                                           read.table("data/chiapet/GM19239/GM19239_merged_replicates.for.BROWSER.spp.z6.broadPeak"),
                                           3, CTCF.hg38)

loops_chiapet_GM19240_clean=clean_all_loops(read.table("data/chiapet/GM19240/GM19240_merged_replicates.e500.clusters.cis.BE3"),
                                            read.table("data/chiapet/GM19240/GM19240_merged_replicates.for.BROWSER.spp.z6.broadPeak"),
                                            3, CTCF.hg38)

# Loops Hi-ChIP
loops_hichip_GM19238_clean=clean_all_loops(read.table("data/hichip/GM19238/GM19238_merged_replicates.e500.clusters.cis.BE3"),
                                            read.table("data/hichip/GM19238/GM19238_merged_replicates.for.BROWSER.spp.z6.broadPeak"),
                                            3, CTCF.hg38)

loops_hichip_GM19239_clean=clean_all_loops(read.table("data/hichip/GM19239/gm19239.e500.clusters.cis.BE3"),
                                            read.table("data/hichip/GM19239/gm19239.for.BROWSER.spp.z6.broadPeak"),
                                            3, CTCF.hg38)

loops_hichip_GM19240_clean=clean_all_loops(read.table("data/hichip/GM19240/gm19240.e500.clusters.cis.BE3"),
                                            read.table("data/hichip/GM19240/gm19240.for.BROWSER.spp.z6.broadPeak"),
                                            3, CTCF.hg38)

```

# Seqrching for the common loops
```{r}
# Inside of the experiment
common_chiapet_38_39_clean=common_loops_new(loops_chiapet_GM19238_clean,
                                            loops_chiapet_GM19239_clean)
common_chiapet_38_40_clean=common_loops_new(loops_chiapet_GM19238_clean,
                                            loops_chiapet_GM19240_clean)
common_chiapet_39_40_clean=common_loops_new(loops_chiapet_GM19239_clean,
                                            loops_chiapet_GM19240_clean)

common_hichip_38_39_clean=common_loops_new(loops_hichip_GM19238_clean,
                                            loops_hichip_GM19239_clean)
common_hichip_38_40_clean=common_loops_new(loops_hichip_GM19238_clean,
                                           loops_hichip_GM19240_clean)
common_hichip_39_40_clean=common_loops_new(loops_hichip_GM19239_clean,
                                           loops_hichip_GM19240_clean)

#Between the experiments
common_chiapet_hichip_38_clean=common_loops_new(loops_chiapet_GM19238_clean,
                                                loops_hichip_GM19238_clean)

common_chiapet_hichip_39_clean=common_loops_new(loops_chiapet_GM19239_clean,
                                                loops_hichip_GM19239_clean)
common_chiapet_hichip_40_clean=common_loops_new(loops_chiapet_GM19240_clean,
                                                loops_hichip_GM19240_clean)
```

# See how PET count affects the loop length
```{r}

results.GM.ctcf.part1[[1]]$PETs_count <- ifelse(results.GM.ctcf.part1[[1]]$score >=10, '>10', '<10')

results.GM.ctcf.part1[[1]]$PETs_count <- as.factor(results.GM.ctcf.part1[[1]]$PETs_count)

results.GM.ctcf.part1.ecdf.weakloops <- ecdf(log(results.GM.ctcf.part1[[1]]$dlugosc_loopow[results.GM.ctcf.part1[[1]]$score<10],10))
results.GM.ctcf.part1.ecdf.strongloops <- ecdf(log(results.GM.ctcf.part1[[1]]$dlugosc_loopow[results.GM.ctcf.part1[[1]]$score>=10],10))

d0 <- ggplot(results.GM.ctcf.part1[[1]])+geom_density(aes(log(dlugosc_loopow,10), color=PETs_count))+
  ggtitle('(Log)Distribution of loops lenghts for strong (PET>=10)\nand weak loops for GM19238 sample')+
  labs(x='Loops lenghts(log10)')+
  scale_color_manual(values=c(color("GM19238_rep1"), color("GM19238_rep2")))+
  theme(axis.text = element_text(size = 12), panel.background = element_rect(fill = NA), 
        panel.grid.major = element_line(colour = "grey90"), axis.title = element_text(size = 12))
  
d0
ggsave(d0, filename = 'Distribution_of_the_loops_length_weak_and_strong_loops_GM19238.png', dpi = 600)
```
