---
title: "manorm_normalization"
---
###

In the presented work only merged replicates were finally shown.
Single replicates, that are mainly needed for the proper functioning of the MAnorm,
result in a high dissimilarity between the Hi-ChIP and ChIA-PET technologies.
It happened because of the different quality of the libraries.

###
# Generation of BED files (peaks and bins)
```{r}

trios=c("GM19238", "GM19239", "GM19240")

### ChIA-PET ###
# Converting peaks.gr into peaks.bed 
for (cell_line in trios){
  write.table(unname(data.frame(seqnames(peaks_with_motif_ChIAPET[[cell_line]]), 
                                start(peaks_with_motif_ChIAPET[[cell_line]]), 
                                end(peaks_with_motif_ChIAPET[[cell_line]]))),
              paste0("data/chiapet/peaks_ChIAPET_", cell_line, ".bed"),
              sep="\t",row.names=FALSE, quote = FALSE)
}

#Generation of bins file
chiapet_bins=IRanges::reduce(unlist(peaks_with_motif_ChIAPET, recursive = TRUE, use.names = TRUE))
write.table(unname(data.frame(seqnames(chiapet_bins),
                              start(chiapet_bins),
                              end(chiapet_bins))),
            paste0("data/chiapet/bins_ChIAPET.bed"),
            sep="\t",row.names=FALSE, quote = FALSE)


### HiChIP ###
cell_lines=c("GM19238", "GM19239", "GM19240")
# Converting peaks.gr into peaks.bed 
for (cell_line in trios){
  write.table(unname(data.frame(seqnames(peaks_with_motif_HiChIP[[cell_line]]), 
                                start(peaks_with_motif_HiChIP[[cell_line]]), 
                                end(peaks_with_motif_HiChIP[[cell_line]]))),
              paste0("data/hichip/peaks_HiChIP_", cell_line, ".bed"),
              sep="\t",row.names=FALSE, quote = FALSE)
}

#Generation of bins file
hichip_bins=IRanges::reduce(unlist(peaks_with_motif_HiChIP, recursive = TRUE, use.names = TRUE))
write.table(unname(data.frame(seqnames(hichip_bins),
                              start(hichip_bins),
                              end(hichip_bins))),
            paste0("data/hichip/bins_HiChIP.bed"),
            sep="\t",row.names=FALSE, quote = FALSE)

### HiChIP 2 replicates ###

cell_lines=c("GM19238_rep1", "GM19238_rep2", "GM19239_rep1", "GM19239_rep2","GM19240_rep1","GM19240_rep2")

for (cell_line in cell_lines){
  write.table(unname(data.frame(seqnames(rep2_peaks_with_motif_HiChIP[[cell_line]]), 
                                start(rep2_peaks_with_motif_HiChIP[[cell_line]]), 
                                end(rep2_peaks_with_motif_HiChIP[[cell_line]]))),
              paste0("data/hichip/peaks_HiChIP_", cell_line, ".bed"),
              sep="\t",row.names=FALSE, quote = FALSE)
}


#Generation of bins file
hichip_bins=IRanges::reduce(unlist(peaks_with_motif_HiChIP, recursive = TRUE, use.names = TRUE))
write.table(unname(data.frame(seqnames(hichip_bins),
                              start(hichip_bins),
                              end(hichip_bins))),
            paste0("data/hichip/bins_HiChIP.bed"),
            sep="\t",row.names=FALSE, quote = FALSE)

### ChIAPET 2 replicates ###

cell_lines=c("GM19238_rep1", "GM19238_rep2", "GM19239_rep1", "GM19239_rep2","GM19240_rep1","GM19240_rep2")

for (cell_line in cell_lines){
  write.table(unname(data.frame(seqnames(rep2_peaks_with_motif_ChIAPET[[cell_line]]), 
                                start(rep2_peaks_with_motif_ChIAPET[[cell_line]]), 
                                end(rep2_peaks_with_motif_ChIAPET[[cell_line]]))),
              paste0("data/chiapet/peaks_ChIAPET_", cell_line, ".bed"),
              sep="\t",row.names=FALSE, quote = FALSE)
}

#Generation of bins file
chiapet_bins=IRanges::reduce(unlist(peaks_with_motif_ChIAPET, recursive = TRUE, use.names = TRUE))
write.table(unname(data.frame(seqnames(chiapet_bins),
                              start(chiapet_bins),
                              end(chiapet_bins))),
            paste0("data/chiapet/bins_ChIAPET.bed"),
            sep="\t",row.names=FALSE, quote = FALSE)

```
###

# [Trial script] MAnorms normalization
```{r}
### ChIA-PET ###
browseVignettes("MAnorm2")
library(MAnorm2)

experiment="chiapet"
manorms_input_chiapet.df=data.frame(read.table(
  paste0("data/", experiment, "/narrow_peaks_profile_bins.xls"), header = T))
norm=normalize(manorms_input_chiapet.df, 4:6, 7:9)

manorms_input_chiapet_ref_bin=data.frame(read.table(paste0("data/", experiment, "/fixed_size_profile_bins.xls"), header = T))
manorms_input_chiapet_ref_bin.gr=GRanges(manorms_input_chiapet_ref_bin)
norm_ref_bins_chiapet=normalize(manorms_input_chiapet_ref_bin, 4:6, 7:9)

# From cluster

norm_inp_chiapet_eden_paired=data.frame(read.table(paste0("data/", experiment, "/ref_bins_paired_profile_bins.xls"), header = T))
norm_chiapet_eden_paired=MAnorm2::normalize(norm_inp_chiapet_eden_paired, 4:6, 7:9)
unique40_chiapet_paired=norm_inp_chiapet_eden_paired[which(norm_inp_chiapet_eden_paired$GM19240.occupancy==1),]
unique40_chiapet_paired[sort(unique40_chiapet_paired$GM19240.read_cnt, index.return=T)$ix,]


norm_inp_chiapet_eden_single=data.frame(read.table(paste0("data/", experiment, "/ref_bins_single_profile_bins.xls"), header = T))
norm_chiapet_eden_single=MAnorm2::normalize(norm_inp_chiapet_eden_single, 4:6, 7:9)
#sort by the lowest value of GM19238.read_cnt
norm_chiapet_eden_single[sort(norm_chiapet_eden_single$GM19238.read_cnt, index.return=T)$ix,]
# Select only true peaks for cell_line
unique40_chiapet=norm_chiapet_eden_single[which(norm_chiapet_eden_single$GM19240.occupancy==1),]
unique40_chiapet[sort(unique40_chiapet$GM19240.read_cnt, index.return=T)$ix,]

unique39_chiapet=norm_chiapet_eden_single[which(norm_chiapet_eden_single$GM19239.occupancy==1),]
unique39_chiapet[sort(unique39_chiapet$GM19239.read_cnt, index.return=T)$ix,]

unique38_chiapet=norm_chiapet_eden_single[which(norm_chiapet_eden_single$GM19238.occupancy==1),]
unique38_chiapet[sort(unique38_chiapet$GM19238.read_cnt, index.return=T)$ix,]



constant_chiapet=norm_chiapet_eden_single[ which(norm_chiapet_eden_single$GM19238.occupancy==1 & 
                                                   norm_chiapet_eden_single$GM19239.occupancy==1 & 
                                                   norm_chiapet_eden_single$GM19240.occupancy==1),]
constant_chiapet[sort(constant_chiapet$GM19238.read_cnt, index.return=T)$ix,]
constant_chiapet[sort(constant_chiapet$GM19239.read_cnt, index.return=T)$ix,]
constant_chiapet[sort(constant_chiapet$GM19240.read_cnt, index.return=T)$ix,]

### with dedup chiapet

norm_inp_chiapet_eden_single_simple=data.frame(read.table(paste0("data/", experiment, "/chiapet_single_simple_profile_bins.xls"), header = T))
norm_chiapet_eden_single_simple=MAnorm2::normalize(norm_inp_chiapet_eden_single_simple, 4:6, 7:9)
#sort by the lowest value of GM19238.read_cnt
norm_chiapet_eden_single_simple[sort(norm_chiapet_eden_single_simple$GM19238.read_cnt, index.return=T)$ix,]
# Select only true peaks for cell_line
unique38_chiapet_simple=norm_chiapet_eden_single_simple[which(norm_chiapet_eden_single_simple$GM19238.occupancy==1),]
unique38_chiapet_simple[sort(unique38_chiapet_simple$GM19238.read_cnt, index.return=T)$ix,]

unique39_chiapet_simple=norm_chiapet_eden_single_simple[which(norm_chiapet_eden_single_simple$GM19239.occupancy==1),]
unique39_chiapet_simple[sort(unique39_chiapet_simple$GM19239.read_cnt, index.return=T)$ix,]

unique40_chiapet_simple=norm_chiapet_eden_single_simple[which(norm_chiapet_eden_single_simple$GM19240.occupancy==1),]
unique40_chiapet_simple[sort(unique40_chiapet_simple$GM19240.read_cnt, index.return=T)$ix,]





constant_chiapet_simple=norm_chiapet_eden_single_simple[ which(norm_chiapet_eden_single_simple$GM19238.occupancy==1 & 
                                                   norm_chiapet_eden_single_simple$GM19239.occupancy==1 & 
                                                   norm_chiapet_eden_single_simple$GM19240.occupancy==1),]
constant_chiapet_simple[sort(constant_chiapet_simple$GM19238.read_cnt, index.return=T)$ix,]
constant_chiapet_simple[sort(constant_chiapet_simple$GM19239.read_cnt, index.return=T)$ix,]
constant_chiapet_simple[sort(constant_chiapet_simple$GM19240.read_cnt, index.return=T)$ix,]


### Workflow proposed by CRAN ###
# One-step normalization
norm=MAnorm2::normalize(norm_inp_chiapet_eden_single_simple, c(4,5,6), c(7,8,9))
raw = log(norm_inp_chiapet_eden_single_simple[4:6] + 0.5, base = 2)

# Plot correlation between the samples
plot(attr(norm, "MA.cor"), symbreaks = TRUE, margins = c(8, 8),
     cexRow = 1, cexCol = 1)

#MA plots
png(paste0('ChIAPET_MAnorm_normalization_.png'), res = 300, width = 4200, height = 4200)
# Generating new plots and data (log2)

par(mar=c(3,3,3,3))
layout(matrix(c(1,2,3,4,5,6,1,7,3,8,5,9),ncol=2),heights=c(1,3,1,3,1,3))
plot.new()
text(0.5,0.5,"GM19238 vs GM19239",cex=3,font=2)
generate_manorm_plot(trios[1:2], norm, raw)
plot.new()
text(0.5,0.5,"GM19238 vs GM19240",cex=3,font=2)
generate_manorm_plot(trios[c(1,3)], norm, raw)
plot.new()
text(0.5,0.5,"GM19239 vs GM19240",cex=3,font=2)
generate_manorm_plot(trios[2:3], norm , raw)
#After normalization
generate_manorm_plot(trios[1:2], norm)
generate_manorm_plot(trios[c(1,3)], norm)
generate_manorm_plot(trios[2:3], norm)
dev.off()

# Converting to bioCond
conds=list(GM19238=bioCond(norm[[4]], norm[[7]], name="GM19238"),
           GM19239=bioCond(norm[[5]], norm[[8]], name="GM19239"),
           GM19240=bioCond(norm[[6]], norm[[9]], name="GM19240"))

### Create a "blind" biocond, to compare two groups and not two samples

# Between 38 and 39
conds$blind_38_39 <- bioCond(norm[c(4, 5)], norm[c(7, 8)], occupy.num = 2,
                       name = "blind_38_39")
conds_38_39 <- fitMeanVarCurve(conds[c(1, 2, 4)], method = "parametric",
                         occupy.only = TRUE, init.coef = c(0.1, 10))
# Visualize mean-variance trend along with the fitted MVC.
plotMeanVarCurve(conds_38_39[3], subset = "occupied", ylim = c(-7, 1))

#Between 38 and 40
conds$blind_38_40 <- bioCond(norm[c(4, 6)], norm[c(7, 9)], occupy.num = 2,
                       name = "blind_38_40")
conds_38_40 <- fitMeanVarCurve(conds[c(1, 3, 5)], method = "parametric",
                         occupy.only = TRUE, init.coef = c(0.1, 10))
# Visualize mean-variance trend along with the fitted MVC.
plotMeanVarCurve(conds_38_40[3], subset = "occupied", ylim = c(-7, 1))

#Between 39 and 40
conds$blind_39_40 <- bioCond(norm[c(5, 6)], norm[c(8, 9)], occupy.num = 2,
                       name = "blind_39_40")
conds_39_40 <- fitMeanVarCurve(conds[c(2, 3, 6)], method = "parametric",
                         occupy.only = TRUE, init.coef = c(0.1, 10))
# Visualize mean-variance trend along with the fitted MVC.
plotMeanVarCurve(conds_39_40[3], subset = "occupied", ylim = c(-7, 1))

# Between all 3 cell-lines
conds$blind_common <- bioCond(norm[c(4, 5, 6)], norm[c(7, 8, 9)], occupy.num = 3,
                       name = "blind_common")
conds_common <- fitMeanVarCurve(conds[c(1, 2, 3, 7)], method = "parametric",
                         occupy.only = TRUE, init.coef = c(0.1, 10))
# Visualize mean-variance trend along with the fitted MVC.
plotMeanVarCurve(conds_common[4], subset = "occupied", ylim = c(-7, 1))



### # Perform differential tests.
res_38_39 <- diffTest(conds_38_39[[1]], conds_38_39[[2]])
res_38_40 <- diffTest(conds_38_40[[1]], conds_38_40[[2]])
res_39_40 <- diffTest(conds_39_40[[1]], conds_39_40[[2]])

MAplot(res_38_39, pval = 0.01, ylim=c(-3, 3), main="GM19238 vs GM19239")
abline(h = 0, lwd = 2, lty = 5, col = "green3")

MAplot(res_38_40, pval = 0.01)
abline(h = 0, lwd = 2, lty = 5, col = "green3")

MAplot(res_39_40, pval = 0.01)
abline(h = 0, lwd = 2, lty = 5, col = "green3")

cor(res_39_40$pval, res_39_40$pval, method = "spearman")


# 3 groups simulaniously

norm <- normalize(norm_inp_chiapet_eden_single_simple, count = 4, occupancy = 7)
norm <- normalize(norm, count = 5, occupancy = 8)
norm <- normalize(norm, count = 6, occupancy = 9)

conds <- list(GM19238 = bioCond(norm[4], norm[7], name = "GM19238"),
              GM19239 = bioCond(norm[5], norm[8], name = "GM19239"),
              GM19240 = bioCond(norm[6], norm[9], name = "GM19240"))

conds_plot <- fitMeanVarCurve(conds[c(1,2, 3,  7)], method = "parametric", occupy.only = TRUE, init.coef = c(0.1, 10))
res <- aovBioCond(conds_plot)
plot(res,  pval = 0.01)
plot(res,  padj = 1e-6, main="GM19238 vs GM19239 vs GM19240")

```

# [ChIA-PET 2 rep] MANorm input
```{r}
# Name of the experiment is being used during the saving of the plots
experiment="ChIA-PET"
# trios names are being used to name the components in the list
cell_lines=c("GM19238_rep1", "GM19238_rep2", "GM19239_rep1", "GM19239_rep2","GM19240_rep1","GM19240_rep2")
trios=c("GM19238", "GM19239", "GM19240")
# read the input file for MANorm (generated from MANorm_utils)
norm_inp_chiapet_2rep=data.frame(read.table(paste0("data/chiapet/chiapet_2rep_wout_reduce_profile_bins.xls"), header = T))

# See how many TRUE/FALSE peaks are present for each cell line for the occupancy calculated by MANorms
table_chiapet_2rep_occupancy_raw=list(
  summary(as.logical(norm_inp_chiapet_2rep$GM19238_rep1.occupancy)),
  summary(as.logical(norm_inp_chiapet_2rep$GM19238_rep2.occupancy)),
  summary(as.logical(norm_inp_chiapet_2rep$GM19239_rep1.occupancy)),
  summary(as.logical(norm_inp_chiapet_2rep$GM19239_rep2.occupancy)),
  summary(as.logical(norm_inp_chiapet_2rep$GM19240_rep1.occupancy)),
  summary(as.logical(norm_inp_chiapet_2rep$GM19240_rep2.occupancy)))
names(table_chiapet_2rep_occupancy_raw)=cell_lines

# Replace the occupancy by occupancy calculated from overlapping with bins
occupancy_by_overlaps_chiapet_2rep=list()
for (cell_line in cell_lines){
  occupancy_by_overlaps_chiapet_2rep[[cell_line]]=as.integer(1:NROW(chiapet_bins) %in% unique(queryHits(findOverlaps(chiapet_bins,rep2_peaks_with_motif_ChIAPET[[cell_line]]))))
}

norm_inp_chiapet_2rep$GM19238_rep1.occupancy=occupancy_by_overlaps_chiapet_2rep$GM19238_rep1
norm_inp_chiapet_2rep$GM19238_rep2.occupancy=occupancy_by_overlaps_chiapet_2rep$GM19238_rep2
norm_inp_chiapet_2rep$GM19239_rep1.occupancy=occupancy_by_overlaps_chiapet_2rep$GM19239_rep1
norm_inp_chiapet_2rep$GM19239_rep2.occupancy=occupancy_by_overlaps_chiapet_2rep$GM19239_rep2
norm_inp_chiapet_2rep$GM19240_rep1.occupancy=occupancy_by_overlaps_chiapet_2rep$GM19240_rep1
norm_inp_chiapet_2rep$GM19240_rep2.occupancy=occupancy_by_overlaps_chiapet_2rep$GM19240_rep2

# See how many TRUE/FALSE peaks are present for each cell line for the occupancy calculated by overlapping
table_chiapet_2rep_occupancy_overlapped=list(
  summary(as.logical(norm_inp_chiapet_2rep$GM19238_rep1.occupancy)),
  summary(as.logical(norm_inp_chiapet_2rep$GM19238_rep2.occupancy)),
  summary(as.logical(norm_inp_chiapet_2rep$GM19239_rep1.occupancy)),
  summary(as.logical(norm_inp_chiapet_2rep$GM19239_rep2.occupancy)),
  summary(as.logical(norm_inp_chiapet_2rep$GM19240_rep1.occupancy)),
  summary(as.logical(norm_inp_chiapet_2rep$GM19240_rep2.occupancy)))
names(table_chiapet_2rep_occupancy_overlapped)=cell_lines

```

#[HiChIP 2 rep] MANorm input
```{r}
# Name of the experiment is being used during the saving of the plots
experiment="HiChIP"
# trios names are being used to name the components in the list
cell_lines=c("GM19238_rep1", "GM19238_rep2", "GM19239_rep1", "GM19239_rep2","GM19240_rep1","GM19240_rep2")
trios=c("GM19238", "GM19239", "GM19240")
# read the input file for MANorm (generated from MANorm_utils)
norm_inp_hichip_2rep=data.frame(read.table(paste0("data/hichip/hichip_2rep_wout_reduce_profile_bins.xls"), header = T))

# See how many TRUE/FALSE peaks are present for each cell line for the occupancy calculated by MANorms
table_hichip_2rep_occupancy_raw=list(
  summary(as.logical(norm_inp_hichip_2rep$GM19238_rep1.occupancy)),
  summary(as.logical(norm_inp_hichip_2rep$GM19238_rep2.occupancy)),
  summary(as.logical(norm_inp_hichip_2rep$GM19239_rep1.occupancy)),
  summary(as.logical(norm_inp_hichip_2rep$GM19239_rep2.occupancy)),
  summary(as.logical(norm_inp_hichip_2rep$GM19240_rep1.occupancy)),
  summary(as.logical(norm_inp_hichip_2rep$GM19240_rep2.occupancy)))
names(table_hichip_2rep_occupancy_raw)=cell_lines

# Replace the occupancy by occupancy calculated from overlapping with bins
occupancy_by_overlaps_hichip_2rep=list()
for (cell_line in cell_lines){
  occupancy_by_overlaps_hichip_2rep[[cell_line]]=as.integer(1:NROW(hichip_bins) %in% unique(queryHits(findOverlaps(hichip_bins,rep2_peaks_with_motif_HiChIP[[cell_line]]))))
}

norm_inp_hichip_2rep$GM19238_rep1.occupancy=occupancy_by_overlaps_hichip_2rep$GM19238_rep1
norm_inp_hichip_2rep$GM19238_rep2.occupancy=occupancy_by_overlaps_hichip_2rep$GM19238_rep2
norm_inp_hichip_2rep$GM19239_rep1.occupancy=occupancy_by_overlaps_hichip_2rep$GM19239_rep1
norm_inp_hichip_2rep$GM19239_rep2.occupancy=occupancy_by_overlaps_hichip_2rep$GM19239_rep2
norm_inp_hichip_2rep$GM19240_rep1.occupancy=occupancy_by_overlaps_hichip_2rep$GM19240_rep1
norm_inp_hichip_2rep$GM19240_rep2.occupancy=occupancy_by_overlaps_hichip_2rep$GM19240_rep2

# See how many TRUE/FALSE peaks are present for each cell line for the occupancy calculated by overlapping
table_hichip_2rep_occupancy_overlapped=list(
  summary(as.logical(norm_inp_hichip_2rep$GM19238_rep1.occupancy)),
  summary(as.logical(norm_inp_hichip_2rep$GM19238_rep2.occupancy)),
  summary(as.logical(norm_inp_hichip_2rep$GM19239_rep1.occupancy)),
  summary(as.logical(norm_inp_hichip_2rep$GM19239_rep2.occupancy)),
  summary(as.logical(norm_inp_hichip_2rep$GM19240_rep1.occupancy)),
  summary(as.logical(norm_inp_hichip_2rep$GM19240_rep2.occupancy)))
names(table_hichip_2rep_occupancy_overlapped)=cell_lines

```

[ChIA-PET 2 rep] MANorm normalization between the replicates
```{r}
### Normalize between groups
norm_chiapet_2rep <- MAnorm2::normalize(norm_inp_chiapet_2rep, count = 4:5, occupancy = 10:11, baseline=5)
norm_chiapet_2rep <- MAnorm2::normalize(norm_chiapet_2rep, count = 6:7, occupancy = 12:13, baseline=7)
norm_chiapet_2rep <- MAnorm2::normalize(norm_chiapet_2rep, count = 8:9, occupancy = 14:15, baseline=9)

# Add information about the index of the peaks, to identify them in the future
norm_chiapet_2rep$index=row.names(norm_chiapet_2rep)

### Visualize the plots before/after normalization (Generating new plots and data (log2))
raw_chiapet_2rep = log(norm_inp_chiapet_2rep[4:9] + 0.5, base = 2)

png(paste0('plots/ChIA-PET_MAnorm_2rep_normalization_mrgBins_y4_wout_reduce_baseline.png'), res = 300, width = 4200, height = 4200)

# Generating new plots and data (log2)
set_xlim<<-c(4,20)
set_ylim<<-c(-4, 4)

par(mar=c(3,3,3,3))
layout(matrix(c(1,2,3,4,5,6,1,7,3,8,5,9),ncol=2),heights=c(1,3,1,3,1,3))
plot.new()
text(0.5,0.5,trios[[1]],cex=3,font=2)
generate_manorm_plot(cell_lines[1:2], norm_chiapet_2rep, raw_chiapet_2rep)
plot.new()
text(0.5,0.5,trios[[2]],cex=3,font=2)
generate_manorm_plot(cell_lines[3:4], norm_chiapet_2rep, raw_chiapet_2rep)
plot.new()
text(0.5,0.5,trios[[3]],cex=3,font=2)
generate_manorm_plot(cell_lines[5:6], norm_chiapet_2rep , raw_chiapet_2rep)
#After normalization
generate_manorm_plot(cell_lines[1:2], norm_chiapet_2rep)
generate_manorm_plot(cell_lines[3:4], norm_chiapet_2rep)
generate_manorm_plot(cell_lines[5:6], norm_chiapet_2rep)
dev.off()
```

#[HiChIP 2 rep] MANorm normalization between the replicates
```{r}
### Normalize between groups
norm_hichip_2rep <- MAnorm2::normalize(norm_inp_hichip_2rep, count = 4:5, occupancy = 10:11)
norm_hichip_2rep <- MAnorm2::normalize(norm_hichip_2rep, count = 6:7, occupancy = 12:13)
norm_hichip_2rep <- MAnorm2::normalize(norm_hichip_2rep, count = 8:9, occupancy = 14:15)
# Add information about the index of the peaks, to identify them in the future
norm_hichip_2rep$index=row.names(norm_hichip_2rep)

### Visualize the plots before/after normalization (Generating new plots and data (log2))
raw_hichip_2rep = log(norm_inp_hichip_2rep[4:9] + 0.5, base = 2)

png(paste0('plots/HiChIP_MAnorm_2rep_normalization_mrgBins_wout_reduce_tr.png'), res = 300, width = 4200, height = 3900)

# Generating new plots and data (log2)
set_xlim<<-c(4,20)
set_ylim<<-c(-4,4)

par(mar=c(3,3,3,3))
layout(matrix(c(1,2,3,4,5,6,1,7,3,8,5,9),ncol=2),heights=c(0.95,3,0.95,3,0.95,3))
plot.new()
text(0.5,0.5,trios[[1]],cex=3,font=2)
generate_manorm_plot(cell_lines[1:2], norm_hichip_2rep, raw_hichip_2rep)
plot.new()
text(0.5,0.5,trios[[2]],cex=3,font=2)
generate_manorm_plot(cell_lines[3:4], norm_hichip_2rep, raw_hichip_2rep)
plot.new()
text(0.5,0.5,trios[[3]],cex=3,font=2)
generate_manorm_plot(cell_lines[5:6], norm_hichip_2rep , raw_hichip_2rep)
#After normalization
generate_manorm_plot(cell_lines[1:2], norm_hichip_2rep)
generate_manorm_plot(cell_lines[3:4], norm_hichip_2rep)
generate_manorm_plot(cell_lines[5:6], norm_hichip_2rep)
dev.off()

```

[ChIA-PET 2 rep] MANorm normalization between the cell lines
```{r}
### Construct a bioCond for each group of samples.
conds_chiapet_2rep_raw <- list(
  GM19238 = bioCond(norm_chiapet_2rep[4:5], norm_chiapet_2rep[10:11], name = trios[[1]], occupy.num = 1),
  GM19239 = bioCond(norm_chiapet_2rep[6:7], norm_chiapet_2rep[12:13], name = trios[[2]], occupy.num = 1),
  GM19240 = bioCond(norm_chiapet_2rep[8:9], norm_chiapet_2rep[14:15], name = trios[[3]], occupy.num = 1))

### Perform between-group normalization.
autosome <- !(norm_inp_chiapet_2rep$chrom %in% c("chrX", "chrY"))
conds_chiapet_2rep <- normBioCond(conds_chiapet_2rep_raw, common.peak.regions = autosome, baseline=2)

png(paste0('plots/',experiment,'_MAnorm_2rep_normalization_info_trial.png'), res = 300, width = 6000, height = 4200)
plot.new()
plot(attr(conds_chiapet_2rep, "MA.cor"), symbreaks = TRUE, margins = c(23, 23), cexRow = 3, cexCol = 3, key.par = list(cex=2.5))
dev.off()

# Drawing MA plots on bioCond objects to visualize the normalization results 
png(paste0('plots/ChIA-PET_MAnorm_2rep_trios_normalization_mrgBins_wout_reduce_trial3.png'), res = 300, width = 4200, height = 4200)
set_xlim<<-c(4,20)
set_ylim<<-c(-2, 2)

# Generating new plots and data (log2)
par(mar=c(3,3,3,3))
layout(matrix(c(1,2,3,4,5,6,1,7,3,8,5,9),ncol=2),heights=c(1,3,1,3,1,3))
plot.new()
text(0.5,0.5,paste0(trios[1]," vs. ", trios[2]),cex=3,font=2)
generate_manorm_plot_trios(trios[1:2], conds_chiapet_2rep_raw, "before")
plot.new()
text(0.5,0.5,paste0(trios[1]," vs. ", trios[3]),cex=3,font=2)
generate_manorm_plot_trios(trios[c(1,3)], conds_chiapet_2rep_raw, "before")
plot.new()
text(0.5,0.5,paste0(trios[2]," vs. ", trios[3]),cex=3,font=2)
generate_manorm_plot_trios(trios[2:3], conds_chiapet_2rep_raw, "before")
#After normalization
generate_manorm_plot_trios(trios[1:2], conds_chiapet_2rep, "after")
generate_manorm_plot_trios(trios[c(1,3)], conds_chiapet_2rep, "after")
generate_manorm_plot_trios(trios[2:3], conds_chiapet_2rep, "after")
dev.off()
```

#[HiChIP 2 rep] MANorm normalization between the cell lines
```{r}
experiment="HiChIP"

### Construct a bioCond for each group of samples.
conds_hichip_2rep_raw <- list(
  bioCond(norm_hichip_2rep[4:5], norm_hichip_2rep[10:11], name = trios[[1]]),
  bioCond(norm_hichip_2rep[6:7], norm_hichip_2rep[12:13], name = trios[[2]]),
  bioCond(norm_hichip_2rep[8:9], norm_hichip_2rep[14:15], name = trios[[3]]))
names(conds_hichip_2rep_raw)=trios

### Perform between-group normalization.
autosome <- !(norm_inp_hichip_2rep$chrom %in% c("chrX", "chrY"))
conds_hichip_2rep <- normBioCond(conds_hichip_2rep_raw, common.peak.regions = autosome)

png(paste0('plots/',experiment,'_MAnorm_2rep_normalization_info.png'), res = 300, width = 6000, height = 4200)
plot.new()
plot(attr(conds_hichip_2rep, "MA.cor"), symbreaks = TRUE, margins = c(23, 23), cexRow = 3, cexCol = 3, key.par = list(cex=2.5))
dev.off()

# Drawing MA plots on bioCond objects to visualize the normalization results 
png(paste0('plots/HiChIP_MAnorm_2rep_trios_normalization_mrgBins_wout_reduce.png'), res = 300, width = 4200, height = 4200)
set_xlim<<-c(4,20)
set_ylim<<-c(-2,2)

# Generating new plots and data (log2)
par(mar=c(3,3,3,3))
layout(matrix(c(1,2,3,4,5,6,1,7,3,8,5,9),ncol=2),heights=c(1,3,1,3,1,3))
plot.new()
text(0.5,0.5,paste0(trios[1]," vs. ", trios[2]),cex=3,font=2)
generate_manorm_plot_trios(trios[1:2], conds_hichip_2rep_raw, "before")
plot.new()
text(0.5,0.5,paste0(trios[1]," vs. ", trios[3]),cex=3,font=2)
generate_manorm_plot_trios(trios[c(1,3)], conds_hichip_2rep_raw, "before")
plot.new()
text(0.5,0.5,paste0(trios[2]," vs. ", trios[3]),cex=3,font=2)
generate_manorm_plot_trios(trios[2:3], conds_hichip_2rep_raw, "before")
#After normalization
generate_manorm_plot_trios(trios[1:2], conds_hichip_2rep, "after")
generate_manorm_plot_trios(trios[c(1,3)], conds_hichip_2rep, "after")
generate_manorm_plot_trios(trios[2:3], conds_hichip_2rep, "after")
dev.off()
```

#[ChIA-PET 2rep] Modeling of Mean-Variance Trend
```{r}
### Fit an MVC.
conds_chiapet_2rep <- fitMeanVarCurve(conds_chiapet_2rep, 
                                     method = "local", 
                                     occupy.only = FALSE,
                                     init.coef = c(0.1, 10)
                                     )

### Plot only occupied genomic intervals,
# as only these intervals have been used to fit the MVC.
plotMeanVarCurve(conds_chiapet_2rep, subset = "all", ylim = c(-7, 0.5))

```

#[HiChIP 2 rep] Modeling of Mean-Variance Trend
```{r}
### Fit an MVC.
conds_hichip_2rep <- fitMeanVarCurve(conds_hichip_2rep, 
                                     method = "local", 
                                     occupy.only = FALSE,
                                     init.coef = c(0.1, 10))
### Plot only occupied genomic intervals,
# as only these intervals have been used to fit the MVC.
plotMeanVarCurve(conds_hichip_2rep, subset = "all", ylim = c(-7, 0.5))
```

#[ChIA-PET 2rep] Differential Tests
```{r}
### Perform differential tests.
res_chiapet_rep2=list(all_trios=aovBioCond(conds_chiapet_2rep),
                     diffTest(conds_chiapet_2rep[[1]], conds_chiapet_2rep[[2]]),
                     diffTest(conds_chiapet_2rep[[1]], conds_chiapet_2rep[[3]]),
                     diffTest(conds_chiapet_2rep[[2]], conds_chiapet_2rep[[3]]))
names(res_chiapet_rep2)=c("all_trios", 
                              paste0(trios[1],"_",trios[2]),
                              paste0(trios[1],"_",trios[3]), 
                              paste0(trios[2],"_",trios[3]))

# Visualize the results
p_value<<- 0.2

png(paste0('plots/ChIA-PET_MAnorm_2rep_trios_diff_test_mrgBins_pval_',p_value,'_regression_all.png'), res = 300, width = 2200, height = 2200)
par(mar=c(2.3,2.3,2.3,2.3))
layout(matrix(c(1,2,3,4,1,5,3,4,1,6,3,4),ncol=3),heights=c(1,3,1,3,1,3))

plot.new()
text(0.5,0.5,"Within paris of trios ",cex=3,font=2)
MAplot(res_chiapet_rep2$GM19238_GM19239, pval = p_value, ylim = c(-2, 2), main=paste0(trios[1]," vs. ", trios[2]), line=0.2)
abline(h = 0, lwd = 2, lty = 5, col = "green3")
plot.new()
text(0.5,0.5,"Within all trios ",cex=3,font=2)
plot(res_chiapet_rep2$all_trios, pval = p_value,line=0.2)
MAplot(res_chiapet_rep2$GM19238_GM19240, pval = p_value,ylim = c(-2, 2), main=paste0(trios[1]," vs. ", trios[3]), line=0.2)
abline(h = 0, lwd = 2, lty = 5, col = "green3")
MAplot(res_chiapet_rep2$GM19239_GM19240, pval = p_value,ylim = c(-2, 2), main=paste0(trios[2]," vs. ", trios[3]),line=0.2)
abline(h = 0, lwd = 2, lty = 5, col = "green3")
dev.off()

```

#[HiChIP 2rep] Differential Tests
```{r}
### Perform differential tests.
res_hichip_rep2=list(aovBioCond(conds_hichip_2rep),
                     diffTest(conds_hichip_2rep[[1]], conds_hichip_2rep[[2]]),
                     diffTest(conds_hichip_2rep[[1]], conds_hichip_2rep[[3]]),
                     diffTest(conds_hichip_2rep[[2]], conds_hichip_2rep[[3]]))
names(res_hichip_rep2)=c("all_trios", 
                         paste0(trios[1],"_",trios[2]),
                         paste0(trios[1],"_",trios[3]), 
                         paste0(trios[2],"_",trios[3]))

# Visualize the results
p_value<<- 0.01

png(paste0('plots/HiChIP_MAnorm_2rep_trios_diff_test_mrgBins_pval_',p_value,'_regression_all.png'), res = 300, width = 2200, height = 2200)
par(mar=c(2.3,2.3,2.3,2.3))
layout(matrix(c(1,2,3,4,1,5,3,4,1,6,3,4),ncol=3),heights=c(1,3,1,3,1,3))

plot.new()
text(0.5,0.5,"Within paris of trios ",cex=3,font=2)
MAplot(res_hichip_rep2$GM19238_GM19239, pval = p_value, ylim = c(-2, 2), main=paste0(trios[1]," vs. ", trios[2]), line=0.2)
abline(h = 0, lwd = 2, lty = 5, col = "green3")
plot.new()
text(0.5,0.5,"Within all trios ",cex=3,font=2)
plot(res_hichip_rep2$all_trios, pval = p_value,line=0.2)
MAplot(res_hichip_rep2$GM19238_GM19240, pval = p_value,ylim = c(-2, 2), main=paste0(trios[1]," vs. ", trios[3]), line=0.2)
abline(h = 0, lwd = 2, lty = 5, col = "green3")
MAplot(res_hichip_rep2$GM19239_GM19240, pval = p_value,ylim = c(-2, 2), main=paste0(trios[2]," vs. ", trios[3]),line=0.2)
abline(h = 0, lwd = 2, lty = 5, col = "green3")
dev.off()
```

# [ChIA-PET 2 rep] Analysis of the results: Show which peaks were filtered by pval based on their mean_value
```{r}
experiment="ChIA-PET"

# Create tables that will include all important information for the analysis
common_chiapet_manorm_2rep=list(
  create_table_common_peaks_with_info(norm_chiapet_2rep, res_chiapet_rep2, conds_chiapet_2rep, trios[1:2]),
  create_table_common_peaks_with_info(norm_chiapet_2rep, res_chiapet_rep2, conds_chiapet_2rep, trios[c(1,3)]),
  create_table_common_peaks_with_info(norm_chiapet_2rep, res_chiapet_rep2, conds_chiapet_2rep, trios[2:3]))
names(common_chiapet_manorm_2rep)=create_short_name_for_col(trios)

# Create additional tables with lower and higher values of mean values (select the squares)
mean_cutoff=10

common_chiapet_manorm_2rep=add_greater_and_lower_mean_ranges_tables(common_chiapet_manorm_2rep, mean_cutoff, trios[1:2])
common_chiapet_manorm_2rep=add_greater_and_lower_mean_ranges_tables(common_chiapet_manorm_2rep, mean_cutoff, trios[c(1,3)])
common_chiapet_manorm_2rep=add_greater_and_lower_mean_ranges_tables(common_chiapet_manorm_2rep, mean_cutoff, trios[2:3])

# Create tables and graphs that will show which mean values have cell lines and their pval                                 
pos_false_tables_chiapet_2rep=list(
  create_fp_tables(common_chiapet_manorm_2rep[[1]],trios[1:2]),
  create_fp_tables(common_chiapet_manorm_2rep[[4]],trios[1:2]),     
  create_fp_tables(common_chiapet_manorm_2rep[[5]],trios[1:2]),
  create_fp_tables(common_chiapet_manorm_2rep[[2]],trios[c(1,3)]),
  create_fp_tables(common_chiapet_manorm_2rep[[6]],trios[c(1,3)]),
  create_fp_tables(common_chiapet_manorm_2rep[[7]],trios[c(1,3)]),
  create_fp_tables(common_chiapet_manorm_2rep[[3]],trios[2:3]),
  create_fp_tables(common_chiapet_manorm_2rep[[8]],trios[2:3]),
  create_fp_tables(common_chiapet_manorm_2rep[[9]],trios[2:3]))

names(pos_false_tables_chiapet_2rep)=names(common_chiapet_manorm_2rep)[c(1,4,5,2,6,7,3,8,9)]


# # Save graphs that will show which mean values have cell lines and their pval
# par="isPval"
# prefix="_2rep_mrgBins"
# 
# save_fp_graphs_with_mean_values(pos_false_tables_chiapet_2rep,trios[1:2], experiment, paste0("all",prefix),par)
# save_fp_graphs_with_mean_values(pos_false_tables_chiapet_2rep,trios[1:2], experiment, paste0("mean>=10",prefix), par)
# save_fp_graphs_with_mean_values(pos_false_tables_chiapet_2rep,trios[1:2], experiment, paste0("mean<10",prefix), par)
# save_fp_graphs_with_mean_values(pos_false_tables_chiapet_2rep,trios[c(1,3)], experiment, paste0("all",prefix), par)
# save_fp_graphs_with_mean_values(pos_false_tables_chiapet_2rep,trios[c(1,3)], experiment, paste0("mean>=10",prefix), par)
# save_fp_graphs_with_mean_values(pos_false_tables_chiapet_2rep,trios[c(1,3)], experiment, paste0("mean<10",prefix), par)
# save_fp_graphs_with_mean_values(pos_false_tables_chiapet_2rep,trios[2:3], experiment, paste0("all",prefix), par)
# save_fp_graphs_with_mean_values(pos_false_tables_chiapet_2rep,trios[2:3], experiment, paste0("mean>=10",prefix), par)
# save_fp_graphs_with_mean_values(pos_false_tables_chiapet_2rep,trios[2:3], experiment, paste0("mean<10",prefix), par)
# rm(prefix)


```

#[HiChIP 2 rep] Analysis of the results: Show which peaks were filtered by pval based on their mean_value
```{r}
experiment="HiChIP"

# Create tables that will include all important information for the analysis
common_hichip_manorm_2rep=list(
  create_table_common_peaks_with_info(norm_hichip_2rep, res_hichip_rep2, conds_hichip_2rep, trios[1:2]),              
  create_table_common_peaks_with_info(norm_hichip_2rep, res_hichip_rep2, conds_hichip_2rep, trios[c(1,3)]),               
  create_table_common_peaks_with_info(norm_hichip_2rep, res_hichip_rep2, conds_hichip_2rep, trios[2:3]))
names(common_hichip_manorm_2rep)=create_short_name_for_col(trios)

# Create additional tables with lower and higher values of mean values (select the squares)
mean_cutoff=10

common_hichip_manorm_2rep=add_greater_and_lower_mean_ranges_tables(common_hichip_manorm_2rep, mean_cutoff, trios[1:2])
common_hichip_manorm_2rep=add_greater_and_lower_mean_ranges_tables(common_hichip_manorm_2rep, mean_cutoff, trios[c(1,3)])
common_hichip_manorm_2rep=add_greater_and_lower_mean_ranges_tables(common_hichip_manorm_2rep, mean_cutoff, trios[2:3])

# Create false pos tables
par="isPval"
prefix="_2rep_mrgRep"

pos_false_tables_hichip_2rep=list(
  create_fp_tables(common_hichip_manorm_2rep[[1]],trios[1:2]),
  create_fp_tables(common_hichip_manorm_2rep[[4]],trios[1:2]),     
  create_fp_tables(common_hichip_manorm_2rep[[5]],trios[1:2]),
  create_fp_tables(common_hichip_manorm_2rep[[2]],trios[c(1,3)]),
  create_fp_tables(common_hichip_manorm_2rep[[6]],trios[c(1,3)]),
  create_fp_tables(common_hichip_manorm_2rep[[7]],trios[c(1,3)]),
  create_fp_tables(common_hichip_manorm_2rep[[3]],trios[2:3]),
  create_fp_tables(common_hichip_manorm_2rep[[8]],trios[2:3]),
  create_fp_tables(common_hichip_manorm_2rep[[9]],trios[2:3]))

names(pos_false_tables_hichip_2rep)=names(common_hichip_manorm_2rep)[c(1,4,5,2,6,7,3,8,9)]
rm(prefix)

# # Save graphs that will show which mean values have cell lines and their pval
# par="isPval"
# prefix="_2rep_mrgBins"
# 
# save_fp_graphs_with_mean_values(pos_false_tables_hichip_2rep,trios[1:2], experiment, paste0("all",prefix),par)
# save_fp_graphs_with_mean_values(pos_false_tables_hichip_2rep,trios[1:2], experiment, paste0("mean>=10",prefix), par)
# save_fp_graphs_with_mean_values(pos_false_tables_hichip_2rep,trios[1:2], experiment, paste0("mean<10",prefix), par)
# save_fp_graphs_with_mean_values(pos_false_tables_hichip_2rep,trios[c(1,3)], experiment, paste0("all",prefix), par)
# save_fp_graphs_with_mean_values(pos_false_tables_hichip_2rep,trios[c(1,3)], experiment, paste0("mean>=10",prefix), par)
# save_fp_graphs_with_mean_values(pos_false_tables_hichip_2rep,trios[c(1,3)], experiment, paste0("mean<10",prefix), par)
# save_fp_graphs_with_mean_values(pos_false_tables_hichip_2rep,trios[2:3], experiment, paste0("all",prefix), par)
# save_fp_graphs_with_mean_values(pos_false_tables_hichip_2rep,trios[2:3], experiment, paste0("mean>=10",prefix), par)
# save_fp_graphs_with_mean_values(pos_false_tables_hichip_2rep,trios[2:3], experiment, paste0("mean<10",prefix), par)
```

[ChIA-PET 2rep] Confusion matrices
```{r}

# List that contains filtered peaks (wout sex chromosomes and peaks that are coming from 3 cell line) 
# They are being used to create confusion matrices
peaks_excl_3_cell_line_and_sex_chr=vector(mode = "list", length = NROW(names(pos_false_tables_chiapet_2rep)))
names(peaks_excl_3_cell_line_and_sex_chr)=names(pos_false_tables_chiapet_2rep)

n=cell1=1
cell2=2

for (pair in names(peaks_excl_3_cell_line_and_sex_chr)){
  tmp1=anti_join(common_chiapet_manorm_2rep[[pair]], 
                 common_chiapet_manorm_2rep[[pair]][common_chiapet_manorm_2rep[[pair]]$chrom=="chrX" |
                                               common_chiapet_manorm_2rep[[pair]]$chrom=="chrY",])
  tmp1=anti_join(tmp1, tmp1[tmp1[[paste0(trios[cell1],".occupancy")]]==0 & 
                         tmp1[[paste0(trios[cell2],".occupancy")]]==0,])
  n=n+1
  if (n==4){cell2=cell2+1}
  if (n==7){cell1=cell1+1}
  
  peaks_excl_3_cell_line_and_sex_chr[[pair]]=tmp1
  rm(tmp1)
}
rm(cell1, cell2, n, pair)

# Create confusion tables for every pairs of replicates and greater and lower ranges                  
confusion_tables_chiapet_2rep=vector(mode="list", length=NROW(peaks_excl_3_cell_line_and_sex_chr))
names(confusion_tables_chiapet_2rep)=names(peaks_excl_3_cell_line_and_sex_chr)
for (i in 1:NROW(confusion_tables_chiapet_2rep)){
  confusion_tables_chiapet_2rep[i]=list(caret::confusionMatrix(factor(peaks_excl_3_cell_line_and_sex_chr[[names(confusion_tables_chiapet_2rep)[i]]]$common_pval, levels=c(TRUE, FALSE)), 
                       factor(peaks_excl_3_cell_line_and_sex_chr[[names(confusion_tables_chiapet_2rep)[i]]]$predicted_rev, levels=c(TRUE, FALSE)),
                       dnn=c(paste0("pval>",p_value), "SPP_detected")))
}

# Collect data for the ROI curve
if (!exists("ROC_curve_chiapet_2rep")){
  ROC_curve_chiapet_2rep=data.frame()
  ROC_curve_chiapet_2rep[nrow(ROC_curve_chiapet_2rep)+length(confusion_tables_chiapet_2rep),]=names(confusion_tables_chiapet_2rep)
  row.names(ROC_curve_chiapet_2rep)=names(confusion_tables_chiapet_2rep)
}

accuracy=c()
for (pair in names(confusion_tables_chiapet_2rep)){
  tmp=confusion_tables_chiapet_2rep[[pair]]$overall[[1]]
  accuracy=c(accuracy, tmp)
}

ROC_curve_chiapet_2rep[,ncol(ROC_curve_chiapet_2rep) + 1]=as.data.frame(accuracy)
colnames(ROC_curve_chiapet_2rep)[ncol(ROC_curve_chiapet_2rep)]=paste0("p_value=",toString(p_value))

# Table that are lying under the confusion matrices (TP, TN, FP, FN)
# 4 CASES
confusion_data_chiapet_2rep=vector(mode="list", length=3)
names(confusion_data_chiapet_2rep)=create_short_name_for_col(trios)

cell1=n=1
cell2=2
for (pair in names(confusion_data_chiapet_2rep)){
  confusion_data_chiapet_2rep[[pair]]=
    # Both show common (TP)
    list(
      TP=peaks_excl_3_cell_line_and_sex_chr[[pair]][peaks_excl_3_cell_line_and_sex_chr[[pair]]$common_pval==TRUE &
                                                      peaks_excl_3_cell_line_and_sex_chr[[pair]][[paste0(trios[cell1], ".occupancy")]]==1 &
                                                      peaks_excl_3_cell_line_and_sex_chr[[pair]][[paste0(trios[cell2], ".occupancy")]]==1,],
      # Spp shows yes, but pval shows different strength (FP)
      FP=peaks_excl_3_cell_line_and_sex_chr[[pair]][peaks_excl_3_cell_line_and_sex_chr[[pair]]$common_pval==FALSE &
                                                      peaks_excl_3_cell_line_and_sex_chr[[pair]][[paste0(trios[cell1], ".occupancy")]]==1 &
                                                      peaks_excl_3_cell_line_and_sex_chr[[pair]][[paste0(trios[cell2], ".occupancy")]]==1,],
      # SPP shows no, but pval shows, że siła jest taka sama (FN)
      FN=peaks_excl_3_cell_line_and_sex_chr[[pair]][peaks_excl_3_cell_line_and_sex_chr[[pair]]$common_pval==TRUE &
                                                      (peaks_excl_3_cell_line_and_sex_chr[[pair]][[paste0(trios[cell1], ".occupancy")]]==0 |
                                                      peaks_excl_3_cell_line_and_sex_chr[[pair]][[paste0(trios[cell2], ".occupancy")]]==0),],
       # SPP shows no and manorm agrees (TN)
       TN=peaks_excl_3_cell_line_and_sex_chr[[pair]][peaks_excl_3_cell_line_and_sex_chr[[pair]]$common_pval==FALSE &
                                                      (peaks_excl_3_cell_line_and_sex_chr[[pair]][[paste0(trios[cell1], ".occupancy")]]==0 |
                                                      peaks_excl_3_cell_line_and_sex_chr[[pair]][[paste0(trios[cell2], ".occupancy")]]==0),])
    n=n+1
    if(n==2){cell2=cell2+1}
    if(n==3){cell1=cell1+1}
}
rm(cell1, cell2, n, pair)
rm(peaks_excl_3_cell_line_and_sex_chr)
```

#[HiChIP 2 rep] Confusion matrices
```{r}
# List that contains filtered peaks (wout sex chromosomes and peaks that are coming from 3 cell line) 
# They are being used to create confusion matrices
peaks_excl_3_cell_line_and_sex_chr=vector(mode = "list", length = NROW(names(pos_false_tables_hichip_2rep)))
names(peaks_excl_3_cell_line_and_sex_chr)=names(pos_false_tables_hichip_2rep)

n=cell1=1
cell2=2

for (pair in names(peaks_excl_3_cell_line_and_sex_chr)){
  tmp1=anti_join(common_hichip_manorm_2rep[[pair]], 
                 common_hichip_manorm_2rep[[pair]][common_hichip_manorm_2rep[[pair]]$chrom=="chrX" |
                                               common_hichip_manorm_2rep[[pair]]$chrom=="chrY",])
  tmp1=anti_join(tmp1, tmp1[tmp1[[paste0(trios[cell1],".occupancy")]]==0 & 
                         tmp1[[paste0(trios[cell2],".occupancy")]]==0,])
  n=n+1
  if (n==4){cell2=cell2+1}
  if (n==7){cell1=cell1+1}
  
  peaks_excl_3_cell_line_and_sex_chr[[pair]]=tmp1
  rm(tmp1)
}
rm(cell1, cell2, n, pair)

# Create confusion tables for every pairs of replicates and greater and lower ranges                  
confusion_tables_hichip_2rep=vector(mode="list", length=NROW(peaks_excl_3_cell_line_and_sex_chr))
names(confusion_tables_hichip_2rep)=names(peaks_excl_3_cell_line_and_sex_chr)
for (i in 1:NROW(confusion_tables_hichip_2rep)){
  confusion_tables_hichip_2rep[i]=list(caret::confusionMatrix(factor(peaks_excl_3_cell_line_and_sex_chr[[names(confusion_tables_hichip_2rep)[i]]]$common_pval, levels=c(TRUE, FALSE)), 
                       factor(peaks_excl_3_cell_line_and_sex_chr[[names(confusion_tables_hichip_2rep)[i]]]$predicted_rev, levels=c(TRUE, FALSE)),
                       dnn=c(paste0("pval>",p_value), "SPP_detected")))
}

# Collect data for the ROI curve
if (!exists("ROC_curve_hichip_2rep")){
  ROC_curve_hichip_2rep=data.frame()
  ROC_curve_hichip_2rep[nrow(ROC_curve_hichip_2rep)+length(confusion_tables_chiapet_2rep),]=names(confusion_tables_chiapet_2rep)
  row.names(ROC_curve_hichip_2rep)=names(confusion_tables_chiapet_2rep)
}

accuracy=c()
for (pair in names(confusion_tables_chiapet_2rep)){
  tmp=confusion_tables_chiapet_2rep[[pair]]$overall[[1]]
  accuracy=c(accuracy, tmp)
}

ROC_curve_hichip_2rep[,ncol(ROC_curve_hichip_2rep) + 1]=as.data.frame(accuracy)
colnames(ROC_curve_hichip_2rep)[ncol(ROC_curve_hichip_2rep)]=paste0("p_value=",toString(p_value))

# Table that are lying under the confusion matrices (TP, TN, FP, FN)
# 4 CASES
confusion_data_hichip_2rep=vector(mode="list", length=3)
names(confusion_data_hichip_2rep)=create_short_name_for_col(trios)

cell1=n=1
cell2=2
for (pair in names(confusion_data_hichip_2rep)){
  confusion_data_hichip_2rep[[pair]]=
    # Both show common (TP)
    list(
      TP=peaks_excl_3_cell_line_and_sex_chr[[pair]][peaks_excl_3_cell_line_and_sex_chr[[pair]]$common_pval==TRUE &
                                                      peaks_excl_3_cell_line_and_sex_chr[[pair]][[paste0(trios[cell1], ".occupancy")]]==1 &
                                                      peaks_excl_3_cell_line_and_sex_chr[[pair]][[paste0(trios[cell2], ".occupancy")]]==1,],
      # Spp shows yes, but pval shows different strength (FP)
      FP=peaks_excl_3_cell_line_and_sex_chr[[pair]][peaks_excl_3_cell_line_and_sex_chr[[pair]]$common_pval==FALSE &
                                                      peaks_excl_3_cell_line_and_sex_chr[[pair]][[paste0(trios[cell1], ".occupancy")]]==1 &
                                                      peaks_excl_3_cell_line_and_sex_chr[[pair]][[paste0(trios[cell2], ".occupancy")]]==1,],
      # SPP shows no, but pval shows, że siła jest taka sama (FN)
      FN=peaks_excl_3_cell_line_and_sex_chr[[pair]][peaks_excl_3_cell_line_and_sex_chr[[pair]]$common_pval==TRUE &
                                                      (peaks_excl_3_cell_line_and_sex_chr[[pair]][[paste0(trios[cell1], ".occupancy")]]==0 |
                                                      peaks_excl_3_cell_line_and_sex_chr[[pair]][[paste0(trios[cell2], ".occupancy")]]==0),],
       # SPP shows no and manorm agrees (TN)
       TN=peaks_excl_3_cell_line_and_sex_chr[[pair]][peaks_excl_3_cell_line_and_sex_chr[[pair]]$common_pval==FALSE &
                                                      (peaks_excl_3_cell_line_and_sex_chr[[pair]][[paste0(trios[cell1], ".occupancy")]]==0 |
                                                      peaks_excl_3_cell_line_and_sex_chr[[pair]][[paste0(trios[cell2], ".occupancy")]]==0),])
    n=n+1
    if(n==2){cell2=cell2+1}
    if(n==3){cell1=cell1+1}
}
rm(cell1, cell2, n, pair)
rm(peaks_excl_3_cell_line_and_sex_chr)

```

#[ChIA-PET 2rep] Select possible constant peaks
```{r}
confusion_data=confusion_data_chiapet_2rep

chiapet_fn_ids=list(
  
  ### PAIRS of cell lines ###
  
  # Probable constant peaks are those, in which peaks for 2 cell lines are TP, and for the third line FN
  # For examples, if GM38_GM39 are TP (by SPP and pval) and GM38_GM40 are negative (by SPP), 
  # but positive by pval (>(0.05)) than those peaks are considered to be constant
  
# Results
  # Between 38_39 and 40 --> + 3510
  # Between 38_40 and 39 --> + 2362
  # Between 39_40 and 38 --> + 3805
  
  fn_38_39=intersect(
    confusion_data$GM38_GM39$TP$norm.index,
    unique(confusion_data$GM38_GM40$FN[confusion_data$GM38_GM40$FN$GM19240.occupancy==FALSE,]$norm.index,
           confusion_data$GM39_GM40$FN[confusion_data$GM39_GM40$FN$GM19240.occupancy==FALSE,]$norm.index)),
  fn_38_40=intersect(
    confusion_data$GM38_GM40$TP$norm.index,
    unique(confusion_data$GM38_GM39$FN[confusion_data$GM38_GM39$FN$GM19239.occupancy==FALSE,]$norm.index,
           confusion_data$GM39_GM40$FN[confusion_data$GM39_GM40$FN$GM19239.occupancy==FALSE,]$norm.index)),
  fn_39_40=intersect(
    confusion_data$GM39_GM40$TP$norm.index,
    unique(confusion_data$GM38_GM39$FN[confusion_data$GM38_GM39$FN$GM19238.occupancy==FALSE,]$norm.index,
           confusion_data$GM38_GM40$FN[confusion_data$GM38_GM40$FN$GM19238.occupancy==FALSE,]$norm.index)),
  
  ### SINGLE CELL LINE ###
  
  # Peaks were 
  
  # Probable constant peaks are those, in which peaks for 2 cell lines are TP, and for the third line FN
  # For examples, if GM38_GM39 are TP (by SPP and pval) and GM38_GM40 are negative (by SPP), 
  # but positive by pval (>(0.05)) than those peaks are considered to be constant
  
# Results
  # Between 38 and other cell_lines --> 8647 vs 9996 >> 6077 common
  # Between 39 and other cell_lines --> 7773 vs 6897 >> 3548 common
  # Between 40 and other cell_lines --> 4770 vs 3701 >> 1174 common
  
  fn_38=intersect(
    confusion_data$GM38_GM39$FN[confusion_data$GM38_GM39$FN$GM19238.occupancy==TRUE,]$norm.index,
    confusion_data$GM38_GM40$FN[confusion_data$GM38_GM40$FN$GM19238.occupancy==TRUE,]$norm.index),

  fn_39=intersect(
    confusion_data$GM38_GM39$FN[confusion_data$GM38_GM39$FN$GM19239.occupancy==TRUE,]$norm.index,
    confusion_data$GM39_GM40$FN[confusion_data$GM39_GM40$FN$GM19239.occupancy==TRUE,]$norm.index),

  fn_40=intersect(
    confusion_data$GM38_GM40$FN[confusion_data$GM38_GM40$FN$GM19240.occupancy==TRUE,]$norm.index,
    confusion_data$GM39_GM40$FN[confusion_data$GM39_GM40$FN$GM19240.occupancy==TRUE,]$norm.index))

### Deduplicate the peaks
# 7807 peaks are constant and were supposed to be unique for PAIRS of cell lines
# with pval=0.03 --> 6047
# with pval=0.06 --> 5620
# with pval=0.15 --> 7498
id_constant_chiapet_by_manorm_peaks_pairs=unique(unlist(chiapet_fn_ids[1:3]))
# 4376 peaks are constant and were supposed to be unique for cell lines
# with pval=0.03 --> 9472
# with pval=0.06 --> 8664
# with pval=0.15 --> 4132
id_constant_chiapet_by_manorm_peaks_single_lines=unique(unlist(chiapet_fn_ids[4:6]))

# Get peaks using their indexes
# 12183 of possible unique peaks
# with pval=0.03 --> 15519 
# with pval=0.06 --> 14284 
# with pval=0.15 --> 11630
# with pval=0.1 --> 11946
constant_chiapet_by_manorm_peaks=norm_chiapet[sort(c(id_constant_chiapet_by_manorm_peaks_pairs, 
                                              id_constant_chiapet_by_manorm_peaks_single_lines)),]

constant_chiapet_by_manorm_peaks.gr=sort(GRanges(constant_chiapet_by_manorm_peaks))

### Overlapping pf the peaks
# 7299 of 11550 are overlaping with ChIP-Seq constant peaks (0.6319481)
# with pval=0.03 --> 9715 of 14524 (0.6688929)
# with pval=0.06 --> 8947 of 13447 (0.6653529) !!
# with pval=0.15 --> 6965 of 11051 (0.6302597)
# with pval=0.1 --> 7167 of 11341 (0.6302597)
# with pval=0.03 --> 7354 of 11637 (0.6319498)
# with pval=0.01 --> 7412 of 11731 (0.6318302)
NROW(subsetByOverlaps(IRanges::reduce(constant_chiapet_by_manorm_peaks.gr+p_exp), IRanges::reduce(common_peaks_for_trios_ChIPSeq$constant_peaks+p_exp)))
NROW(IRanges::reduce(constant_chiapet_by_manorm_peaks.gr+p_exp))

# 31 of 7299 are actually overlaping with SPP detected peaks, 
# but for some reason had false occupancy (some of them are narrow)
subsetByOverlaps(constant_chiapet_by_manorm_peaks.gr, common_peaks_for_trios_ChIAPET$constant_peaks)

# That's why we want to reduce these peaks. In total we have 39031 (19333+19698) peaks, 
# after reduction 36600 
# with pval=0.03 --> 39967
# with pval=0.06 --> 38732
# with pval=0.15 --> 36047 
chiapet_constant_peaks_with_manorm=IRanges::reduce(c(constant_chiapet_by_manorm_peaks.gr, common_peaks_for_trios_ChIAPET$constant_peaks))

# How many initial peaks from ChIA-PET are overlapping with ChIP-Seq constant peaks
# 21981 of 22818 (0.9633184)
subsetByOverlaps(IRanges::reduce(common_peaks_for_trios_ChIAPET$constant_peaks+p_exp), IRanges::reduce(common_peaks_for_trios_ChIPSeq$constant_peaks+p_exp))

# Let's do the overlap of all true peaks with ChIP-Seq constant peaks
# 26628 from 31307 were overlapped (before only 23037, so +3591 new peaks), ChIP-Seq has 37332 peaks. (0.8505446)
# with pval=0.03 --> 28310 from 33453 (0.8462619)
# with pval=0.06 --> 27786 from 32642 (0.8512346)
# with pval=0.15 --> 26354 from 30876 (0.8535432)
NROW(subsetByOverlaps(IRanges::reduce(chiapet_constant_peaks_with_manorm+p_exp), IRanges::reduce(common_peaks_for_trios_ChIPSeq$constant_peaks+p_exp)))
NROW(IRanges::reduce(chiapet_constant_peaks_with_manorm+p_exp))

# Check which new peaks were being  ADDITIONALY detected by manorm
subsetByOverlaps(chiapet_constant_peaks_with_manorm, common_peaks_for_trios_ChIAPET$constant_peaks, invert=TRUE)

```

# [HiChIP 2rep] Select possible constant peaks
```{r}

pos_false_table=pos_false_tables_hichip_2rep

### Were unique for pairs of cell lines
# Between 38_39 and 40 --> + 1017
# Between 38_40 and 39 --> + 2377
# Between 39_40 and 38 --> + 722

hichip_fn_ids=list(
  fn_38_39=intersect(
  row.names(pos_false_table[[1]][[1]]),
  unique(row.names(pos_false_table[[4]][[4]][pos_false_table[[4]][[4]]$common_pval==TRUE,]),
              row.names(pos_false_table[[7]][[4]][pos_false_table[[7]][[4]]$common_pval==TRUE,]))),
  fn_38_40=intersect(
  row.names(pos_false_table[[4]][[1]]),
  unique(row.names(pos_false_table[[1]][[4]][pos_false_table[[1]][[4]]$common_pval==TRUE,]),
              row.names(pos_false_table[[7]][[5]][pos_false_table[[7]][[5]]$common_pval==TRUE,]))),
  
  fn_39_40=intersect(
  row.names(pos_false_table[[7]][[1]]),
  unique(row.names(pos_false_table[[1]][[5]][pos_false_table[[1]][[5]]$common_pval==TRUE,]),
              row.names(pos_false_table[[4]][[5]][pos_false_table[[4]][[5]]$common_pval==TRUE,]))),
  
### Were unique for each cell_line
# Between 38 and other cell_lines --> 4266 vs 2911 >> 1729 common
# Between 39 and other cell_lines --> 1136 vs 1450 >> 375 common
# Between 40 and other cell_lines --> 4041 vs 5912 >> 3253 common
  
  fn_38=intersect(
    row.names(pos_false_table[[1]]$false_peaks[pos_false_table[[1]]$false_peaks$common_pval==TRUE &                                           
                                               pos_false_table[[1]]$false_peaks[[paste0(trios[[1]],".occupancy")]]==TRUE & 
                                               pos_false_table[[1]]$false_peaks[[paste0(trios[[2]],".occupancy")]]==FALSE ,]),
    row.names(pos_false_table[[4]]$false_peaks[pos_false_table[[4]]$false_peaks$common_pval==TRUE &                                               
                                               pos_false_table[[4]]$false_peaks[[paste0(trios[[1]],".occupancy")]]==TRUE &
                                               pos_false_table[[4]]$false_peaks[[paste0(trios[[3]],".occupancy")]]==FALSE,])),
  fn_39=intersect(
    row.names(pos_false_table[[1]]$false_peaks[pos_false_table[[1]]$false_peaks$common_pval==TRUE &                                             
                                               pos_false_table[[1]]$false_peaks[[paste0(trios[[1]],".occupancy")]]==FALSE &
                                               pos_false_table[[1]]$false_peaks[[paste0(trios[[2]],".occupancy")]]==TRUE,]),
    row.names(pos_false_table[[7]]$false_peaks[pos_false_table[[7]]$false_peaks$common_pval==TRUE &                                                
                                               pos_false_table[[7]]$false_peaks[[paste0(trios[[2]],".occupancy")]]==TRUE &
                                               pos_false_table[[7]]$false_peaks[[paste0(trios[[3]],".occupancy")]]==FALSE,])),
  fn_40=intersect(
    row.names(pos_false_table[[4]]$false_peaks[pos_false_table[[4]]$false_peaks$common_pval==TRUE &                                              
                                               pos_false_table[[4]]$false_peaks[[paste0(trios[[1]],".occupancy")]]==FALSE & 
                                               pos_false_table[[4]]$false_peaks[[paste0(trios[[3]],".occupancy")]]==TRUE,]),
    row.names(pos_false_table[[7]]$false_peaks[pos_false_table[[7]]$false_peaks$common_pval==TRUE &                                                
                                               pos_false_table[[7]]$false_peaks[[paste0(trios[[2]],".occupancy")]]==FALSE & 
                                               pos_false_table[[7]]$false_peaks[[paste0(trios[[3]],".occupancy")]]==TRUE,])))

### Duplicate the peaks
# 1752 peaks are constant and were supposed to be unique for PAIRS of cell lines
id_constant_hichip_by_manorm_peaks_pairs=unique(unlist(hichip_fn_ids[1:3]))
# 1069 peaks are constant and were supposed to be unique for cell lines
id_constant_hichip_by_manorm_peaks_single_lines=unique(unlist(hichip_fn_ids[4:6]))


# 2821 in total
constant_hichip_by_manorm_peaks=norm_hichip[c(id_constant_hichip_by_manorm_peaks_pairs, 
                                              id_constant_hichip_by_manorm_peaks_single_lines),]

constant_hichip_by_manorm_peaks.gr=sort(GRanges(constant_hichip_by_manorm_peaks))


### Overlapping pf the peaks
# 1857 of 2761 are overlaping with ChIP-Seq (0.6725824)
# p_val=10^-8 --> 5063 of 7508 (0.6743474)
# p_val=10^-7 --> 4881 of 7188 (0.6790484)
# p_val=10^-6 --> 4637 of 6752 (0.6790484)
# p_val=10^-9 --> 5191 of 7757 (0.669202)
# p_val=10^-5 --> 4278 of 6193 (0.6907799)
# p_val=10^-4 --> 3854 of 5566 (0.6924183)
# p_val=10^-2 --> 2506 of 3672 (0.6824619)
NROW(subsetByOverlaps(IRanges::reduce(constant_hichip_by_manorm_peaks.gr+p_exp), IRanges::reduce(common_peaks_for_trios_ChIPSeq$constant_peaks+p_exp)))
NROW(IRanges::reduce(constant_hichip_by_manorm_peaks.gr+p_exp))

# 182 of 2761 are actually overlaping with SPP detected peaks, but for some reason had false occupancy
NROW(subsetByOverlaps(constant_hichip_by_manorm_peaks.gr, common_peaks_for_trios_HiChIP$constant_peaks))

# That's why we want to reduce these peaks. In total we have x peaks, after reduction 27580 (2 more peaks were detected as overlapped)
hichip_constant_peaks_with_manorm=IRanges::reduce(c(constant_hichip_by_manorm_peaks.gr, common_peaks_for_trios_HiChIP$constant_peaks))

# How many initial peaks from ChIA-PET are overlapping with ChIP-Seq constant peaks
# 22514 of 23227 (0.969303)
NROW(subsetByOverlaps(IRanges::reduce(common_peaks_for_trios_HiChIP$constant_peaks+p_exp), IRanges::reduce(common_peaks_for_trios_ChIPSeq$constant_peaks+p_exp)))
NROW(IRanges::reduce(common_peaks_for_trios_HiChIP$constant_peaks+p_exp))

# Let's do the overlap of all true peaks with ChIP-Seq constant peaks
# 23648 from 25116 were overlapped (before only 22514, so +1134 new peaks), ChIP-Seq has 37332 peaks. (0.9415512)
# with pval=0.03 --> 28310 from 33453 (0.8462619)
# with pval=0.06 --> 27786 from 32642 (0.8512346)
NROW(subsetByOverlaps(IRanges::reduce(hichip_constant_peaks_with_manorm+p_exp), IRanges::reduce(common_peaks_for_trios_ChIPSeq$constant_peaks+p_exp)))
NROW(IRanges::reduce(hichip_constant_peaks_with_manorm+p_exp))

# Check which new peaks were being  ADDITIONALY detected by manorm
NROW(subsetByOverlaps(hichip_constant_peaks_with_manorm, common_peaks_for_trios_HiChIP$constant_peaks, invert=TRUE))



# Let's do the overlap of all true peaks with ChIP-Seq all peaks
# p_value=0.05 --> 0.9644848 (they are not from proper groups)
NROW(subsetByOverlaps(IRanges::reduce(hichip_constant_peaks_with_manorm+p_exp), IRanges::reduce(unlist(common_peaks_for_trios_ChIPSeq+p_exp))))
NROW(IRanges::reduce(hichip_constant_peaks_with_manorm+p_exp))



```

###################################################################################################################################################

# [ChIA-PET merged] MANorm input
```{r}
# Name of the experiment is being used during the saving of the plots
experiment="ChIA-PET"
# trios names are being used to name the components in the list
trios=c("GM19238", "GM19239", "GM19240")
# read the input file for MANorm (generated from MANorm_utils)
norm_inp_chiapet=data.frame(read.table(paste0("data/chiapet/chiapet_merged_wout_reduce_profile_bins.xls"), header = T))

# See how many TRUE/FALSE peaks are present for each cell line for the occupancy calculated by MANorms
table_chiapet_occupancy_raw=list(
  summary(as.logical(norm_inp_chiapet$GM19238.occupancy)),
  summary(as.logical(norm_inp_chiapet$GM19239.occupancy)),
  summary(as.logical(norm_inp_chiapet$GM19240.occupancy)))
names(table_chiapet_occupancy_raw)=trios

# Replace the occupancy by occupancy calculated from overlapping with bins
occupancy_by_overlaps_chiapet=list()
for (cell_line in trios){
  occupancy_by_overlaps_chiapet[[cell_line]]=as.integer(1:NROW(chiapet_bins) %in% unique(queryHits(findOverlaps(chiapet_bins,peaks_with_motif_ChIAPET[[cell_line]]))))
}

norm_inp_chiapet$GM19238.occupancy=occupancy_by_overlaps_chiapet$GM19238
norm_inp_chiapet$GM19239.occupancy=occupancy_by_overlaps_chiapet$GM19239
norm_inp_chiapet$GM19240.occupancy=occupancy_by_overlaps_chiapet$GM19240

# See how many TRUE/FALSE peaks are present for each cell line for the occupancy calculated by overlapping
table_chiapet_occupancy_overlapped=list(
  summary(as.logical(norm_inp_chiapet$GM19238.occupancy)),
  summary(as.logical(norm_inp_chiapet$GM19239.occupancy)),
  summary(as.logical(norm_inp_chiapet$GM19240.occupancy)))
names(table_chiapet_occupancy_overlapped)=trios

```

#[HiChIP merged] MANorm input 
```{r}
# Name of the experiment is being used during the saving of the plots
experiment="HiChIP"
# trios names are being used to name the components in the list
trios=c("GM19238", "GM19239", "GM19240")
# read the input file for MANorm (generated from MANorm_utils)
norm_inp_hichip=data.frame(read.table(paste0("data/hichip/hichip_merged_wout_reduce_profile_bins.xls"), header = T))

# See how many TRUE/FALSE peaks are present for each cell line for the occupancy calculated by MANorms
table_hichip_occupancy_raw=list(
  summary(as.logical(norm_inp_hichip$GM19238.occupancy)),
  summary(as.logical(norm_inp_hichip$GM19239.occupancy)),
  summary(as.logical(norm_inp_hichip$GM19240.occupancy)))
names(table_hichip_occupancy_raw)=trios

# Replace the occupancy by occupancy calculated from overlapping with bins
occupancy_by_overlaps_hichip=list()
for (cell_line in trios){
  occupancy_by_overlaps_hichip[[cell_line]]=as.integer(1:NROW(hichip_bins) %in% unique(queryHits(findOverlaps(hichip_bins,peaks_with_motif_HiChIP[[cell_line]]))))
}

norm_inp_hichip$GM19238.occupancy=occupancy_by_overlaps_hichip$GM19238
norm_inp_hichip$GM19239.occupancy=occupancy_by_overlaps_hichip$GM19239
norm_inp_hichip$GM19240.occupancy=occupancy_by_overlaps_hichip$GM19240

# See how many TRUE/FALSE peaks are present for each cell line for the occupancy calculated by overlapping
table_hichip_occupancy_overlapped=list(
  summary(as.logical(norm_inp_hichip$GM19238.occupancy)),
  summary(as.logical(norm_inp_hichip$GM19239.occupancy)),
  summary(as.logical(norm_inp_hichip$GM19240.occupancy)))
names(table_hichip_occupancy_overlapped)=trios

```

# [ChIA-PET merged] MANorm normalization between the cell lines
```{r}
### Visualize the plots before/after normalization (log2)
raw_chiapet = log(norm_inp_chiapet[4:6] + 0.5, base = 2)

### Normalize between cell lines
autosome <- !(norm_inp_chiapet$chrom %in% c("chrX", "chrY"))
norm_chiapet <- normalize(norm_inp_chiapet, c(4:6), c(7:9), common.peak.regions = autosome)
# Add information about the index of the peaks, to identify them in the future
norm_chiapet$index=row.names(norm_chiapet)

png(paste0('plots/',experiment,'_MAnorm_merRep_normalization_info.png'), res = 300, width = 6000, height = 4200)
plot.new()
plot(attr(norm_chiapet, "MA.cor"), symbreaks = TRUE, margins = c(23, 23), cexRow = 3, cexCol = 3, key.par = list(cex=2.5))
dev.off()

png(paste0('plots/',experiment,'_MAnorm_merRep_normalization_overlaps_wout_reduce.png'), res = 300, width = 4200, height = 4200)

# Generation of new plots before/after normalization (log2)
set_xlim<<-c(6,20)
set_ylim<<-c(-2,2)

par(mar=c(3,3,3,3))
layout(matrix(c(1,2,3,4,5,6,1,7,3,8,5,9),ncol=2),heights=c(1,3,1,3,1,3))
plot.new()
text(0.5,0.5,paste0(trios[1],' vs. ', trios[2]),cex=3,font=2)
generate_manorm_plot(trios[1:2], norm_chiapet, raw_chiapet)
plot.new()
text(0.5,0.5,paste0(trios[1],' vs. ', trios[3]),cex=3,font=2)
generate_manorm_plot(trios[c(1,3)], norm_chiapet, raw_chiapet)
plot.new()
text(0.5,0.5,paste0(trios[2],' vs. ', trios[3]),cex=3,font=2)
generate_manorm_plot(trios[2:3], norm_chiapet , raw_chiapet)
#After normalization
generate_manorm_plot(trios[1:2], norm_chiapet)
generate_manorm_plot(trios[c(1,3)], norm_chiapet)
generate_manorm_plot(trios[2:3], norm_chiapet)
dev.off()
```

#[HiChIP merged] MANorm normalization between the cell lines
```{r}
### Visualize the plots before/after normalization (Generating new plots and data (log2))
raw_hichip = log(norm_inp_hichip[4:6] + 0.5, base = 2)

### Normalize between cell lines
autosome <- !(norm_inp_hichip$chrom %in% c("chrX", "chrY"))
norm_hichip <- normalize(norm_inp_hichip, c(4:6), c(7:9), common.peak.regions = autosome)
# Add information about the index of the peaks, to identify them in the future
norm_hichip$index=row.names(norm_hichip)

png(paste0('plots/',experiment,'_MAnorm_merRep_normalization_info.png'), res = 300, width = 6000, height = 4200)
plot.new()
plot(attr(norm_hichip, "MA.cor"), symbreaks = TRUE, margins = c(23, 23), cexRow = 3, cexCol = 3, key.par = list(cex=2.5))
dev.off()


png(paste0('plots/HiChIP_MAnorm_merRep_normalization_overlaps_wout_reduce.png'), res = 300, width = 4200, height = 4200)

# Generating new plots and data (log2)
set_xlim<<-c(6,20)
set_ylim<<-c(-2,2)

par(mar=c(3,3,3,3))
layout(matrix(c(1,2,3,4,5,6,1,7,3,8,5,9),ncol=2),heights=c(1,3,1,3,1,3))
plot.new()
text(0.5,0.5,paste0(trios[1],' vs. ', trios[2]),cex=3,font=2)
generate_manorm_plot(trios[1:2], norm_hichip, raw_hichip)
plot.new()
text(0.5,0.5,paste0(trios[1],' vs. ', trios[3]),cex=3,font=2)
generate_manorm_plot(trios[c(1,3)], norm_hichip, raw_hichip)
plot.new()
text(0.5,0.5,paste0(trios[2],' vs. ', trios[3]),cex=3,font=2)
generate_manorm_plot(trios[2:3], norm_hichip , raw_hichip)
#After normalization
generate_manorm_plot(trios[1:2], norm_hichip)
generate_manorm_plot(trios[c(1,3)], norm_hichip)
generate_manorm_plot(trios[2:3], norm_hichip)
dev.off()
```

#[ChIA-PET merged] Modeling of Mean-Variance Trend
```{r}
### Construct a bioCond for each group of samples.
conds_chiapet <- list(
  bioCond(norm_chiapet[4], norm_chiapet[7], name = trios[1]),
  bioCond(norm_chiapet[5], norm_chiapet[8], name = trios[2]),
  bioCond(norm_chiapet[6], norm_chiapet[9], name = trios[3]))
names(conds_chiapet)=trios

### Create a "blind" biocond, that will treat two samples as replicates.
# Only common peak regions of the two samples are considered to the occupied by the "Blind" bioCond

conds_chiapet$blind_1 <- bioCond(norm_chiapet[c(4, 5)], norm_chiapet[c(7, 8)], occupy.num = 2)
conds_chiapet$blind_2 <- bioCond(norm_chiapet[c(4, 6)], norm_chiapet[c(7, 9)], occupy.num = 2)
conds_chiapet$blind_3 <- bioCond(norm_chiapet[c(5, 6)], norm_chiapet[c(8, 9)], occupy.num = 2)
conds_chiapet$blind_common <- bioCond(norm_chiapet[c(4, 5, 6)], norm_chiapet[c(7, 8, 9)], occupy.num = 3)

names(conds_chiapet)[4:7]=c(paste0("blind_", trios[1],"_",trios[2]), 
                           paste0("blind_", trios[1],"_",trios[3]),
                           paste0("blind_", trios[2],"_",trios[3]),
                           "blind_common")

conds_chiapet_meanCurve=list(fitMeanVarCurve(conds_chiapet[c(1, 2, 3, 7)], method = "param",
                         occupy.only = FALSE, init.coef = c(0.1, 10)),
                            fitMeanVarCurve(conds_chiapet[c(1, 2, 4)], method = "param",
                         occupy.only = FALSE, init.coef = c(0.1, 10)),
                            fitMeanVarCurve(conds_chiapet[c(1, 3, 5)], method = "param",
                         occupy.only = FALSE, init.coef = c(0.1, 10)),
                            fitMeanVarCurve(conds_chiapet[c(2, 3, 6)], method = "param",
                         occupy.only = FALSE, init.coef = c(0.1, 10)))
names(conds_chiapet_meanCurve)=c("all_trios", 
                                 paste0(trios[1],"_",trios[2]),
                                 paste0(trios[1],"_",trios[3]), 
                                 paste0(trios[2],"_",trios[3]))

# Visualize mean-variance trend along with the fitted MVC. Plots are not being saved
# plotMeanVarCurve(conds_chiapet_meanCurve[[2]][3], subset = "all", ylim = c(-7, 1))
# plotMeanVarCurve(conds_chiapet_meanCurve[[3]][3], subset = "all", ylim = c(-7, 1))
# plotMeanVarCurve(conds_chiapet_meanCurve[[4]][3], subset = "all", ylim = c(-7, 1))
# plotMeanVarCurve(conds_chiapet_meanCurve$all_trios[4], subset = "all", ylim = c(-7, 1))

```

#[HiChIP merged] Modeling of Mean-Variance Trend
```{r}
### Construct a bioCond for each group of samples.
conds_hichip <- list(
  bioCond(norm_hichip[4], norm_hichip[7], name = trios[1]),
  bioCond(norm_hichip[5], norm_hichip[8], name = trios[2]),
  bioCond(norm_hichip[6], norm_hichip[9], name = trios[3]))
names(conds_hichip)=trios

### Create a "blind" biocond, that will treat two samples as replicates.
# Only common peak regions of the two samples are considered to the occupied by the "Blind" bioCond

conds_hichip$blind_1 <- bioCond(norm_hichip[c(4, 5)], norm_hichip[c(7, 8)], occupy.num = 2)
conds_hichip$blind_2 <- bioCond(norm_hichip[c(4, 6)], norm_hichip[c(7, 9)], occupy.num = 2)
conds_hichip$blind_3 <- bioCond(norm_hichip[c(5, 6)], norm_hichip[c(8, 9)], occupy.num = 2)
conds_hichip$blind_common <- bioCond(norm_hichip[c(4, 5, 6)], norm_hichip[c(7, 8, 9)], occupy.num = 3)

names(conds_hichip)[4:7]=c(paste0("blind_", trios[1],"_",trios[2]), 
                           paste0("blind_", trios[1],"_",trios[3]),
                           paste0("blind_", trios[2],"_",trios[3]),
                           "blind_common")

conds_hichip_meanCurve=list(fitMeanVarCurve(conds_hichip[c(1, 2, 3, 7)], method = "param",
                         occupy.only = FALSE, init.coef = c(0.1, 10)),
                            fitMeanVarCurve(conds_hichip[c(1, 2, 4)], method = "param",
                         occupy.only = FALSE, init.coef = c(0.1, 10)),
                            fitMeanVarCurve(conds_hichip[c(1, 3, 5)], method = "param",
                         occupy.only = FALSE, init.coef = c(0.1, 10)),
                            fitMeanVarCurve(conds_hichip[c(2, 3, 6)], method = "param",
                         occupy.only = FALSE, init.coef = c(0.1, 10)))
names(conds_hichip_meanCurve)=c("all_trios", 
                                     paste0(trios[1],"_",trios[2]),
                                     paste0(trios[1],"_",trios[3]),
                                     paste0(trios[2],"_",trios[3]))

# Visualize mean-variance trend along with the fitted MVC.Plots are not being saved
plotMeanVarCurve(conds_hichip_meanCurve[[2]][3], subset = "occupied", ylim = c(-7, 1))
plotMeanVarCurve(conds_hichip_meanCurve[[3]][3], subset = "occupied", ylim = c(-7, 1))
plotMeanVarCurve(conds_hichip_meanCurve[[4]][3], subset = "occupied", ylim = c(-7, 1))
plotMeanVarCurve(conds_hichip_meanCurve$all_trios[4], subset = "occupied", ylim = c(-7, 1))

```

#[ChIA-PET merged] Differential Tests
```{r}
experiment="ChIA-PET"
### Perform differential tests
res_chiapet=list(
  aovBioCond(conds_chiapet_meanCurve[[1]]),
  diffTest(conds_chiapet_meanCurve[[2]][[1]], conds_chiapet_meanCurve[[2]][[2]]),
  diffTest(conds_chiapet_meanCurve[[3]][[1]], conds_chiapet_meanCurve[[3]][[2]]),
  diffTest(conds_chiapet_meanCurve[[4]][[1]], conds_chiapet_meanCurve[[4]][[2]]))
names(res_chiapet)=names(conds_chiapet_meanCurve)

# Visualize the results
p_value<<- 0.05

png(paste0('plots/',experiment,'_MAnorm_merRep_trios_diff_test_pval_',p_value,'_parametric_all.png'), res = 300, width = 2200, height = 2200)
par(mar=c(2.3,2.3,2.3,2.3))
layout(matrix(c(1,2,3,4,1,5,3,4,1,6,3,4),ncol=3),heights=c(1,3,1,3,1,3))

plot.new()
text(0.5,0.5,"Within paris of trios ",cex=3,font=2)
MAplot(res_chiapet[[2]], pval = p_value, ylim = c(-2, 2), main=paste0(trios[1]," vs. ",trios[2]), line=0.2)
abline(h = 0, lwd = 2, lty = 5, col = "green3")
plot.new()
text(0.5,0.5,"Within all trios ",cex=3,font=2)
plot(res_chiapet[[1]], pval = p_value,line=0.2)
MAplot(res_chiapet[[3]], pval = p_value,ylim = c(-2, 2), main=paste0(trios[1]," vs. ",trios[3]), line=0.2)
abline(h = 0, lwd = 2, lty = 5, col = "green3")
MAplot(res_chiapet[[4]], pval = p_value,ylim = c(-2, 2), main=paste0(trios[2]," vs. ",trios[3]),line=0.2)
abline(h = 0, lwd = 2, lty = 5, col = "green3")
dev.off()

```

#[HiChIP merged] Differential Tests
```{r}
experiment="HiChIP"
### # Perform differential tests
res_hichip=list(
  aovBioCond(conds_hichip_meanCurve$all_trios),
  diffTest(conds_hichip_meanCurve[[2]][[1]], conds_hichip_meanCurve[[2]][[2]]),
  diffTest(conds_hichip_meanCurve[[3]][[1]], conds_hichip_meanCurve[[3]][[2]]),
  diffTest(conds_hichip_meanCurve[[4]][[1]], conds_hichip_meanCurve[[4]][[2]]))
names(res_hichip)=names(conds_hichip_meanCurve)

# Visualize the results
p_value<<- 0.05

png(paste0('plots/',experiment,'_MAnorm_merRep_trios_diff_test_pval_',p_value,'_parametric_all.png'), res = 300, width = 2200, height = 2200)
par(mar=c(2.3,2.3,2.3,2.3))
layout(matrix(c(1,2,3,4,1,5,3,4,1,6,3,4),ncol=3),heights=c(1,3,1,3,1,3))

plot.new()
text(0.5,0.5,"Within paris of trios ",cex=3,font=2)
MAplot(res_hichip$GM19238_GM19239, pval = p_value, ylim = c(-2, 2), main=paste0(trios[1]," vs. ", trios[2]), line=0.2)
abline(h = 0, lwd = 2, lty = 5, col = "green3")
plot.new()
text(0.5,0.5,"Within all trios ",cex=3,font=2)
plot(res_hichip$all_trios, pval = p_value,line=0.2)
MAplot(res_hichip$GM19238_GM19240, pval = p_value,ylim = c(-2, 2), main=paste0(trios[1]," vs. ", trios[3]), line=0.2)
abline(h = 0, lwd = 2, lty = 5, col = "green3")
MAplot(res_hichip$GM19239_GM19240, pval = p_value,ylim = c(-2, 2), main=paste0(trios[2]," vs. ", trios[3]),line=0.2)
abline(h = 0, lwd = 2, lty = 5, col = "green3")
dev.off()
```

#[ChIA-PET merged] Differential Tests - statistical power of identifying differential genomic intervals for merged and single replicates
```{r}

#Define the correlation between single and merged replicates
correaltion_chiapet_mer_vs_2rep=c()
for (name in names(res_chiapet)){
  correaltion_chiapet_mer_vs_2rep[[name]]=cor(res_chiapet_rep2[[name]]$pval, res_chiapet[[name]]$pval, method = "spearman")
}

png(paste0('plots/',experiment,'_correlation_pval_single_merged_wout_reduce.png'), res = 300, width = 2200, height = 1100)
layout(matrix(c(1,3,7,2,4,8,2,5,9,2,6,10),ncol=4),heights=c(1,3,0.5,1,3,0.5,1,3,0.5,1,3,0.5), widths=c(2, 1.5, 1.5, 1.5))

par(mar=c(0,0,0,0))
plot.new()
text(0.5,0.5,"All trios",cex=1.5,font=2)
plot.new()
text(0.5,0.5,"Within pairs of trios",cex=1.5,font=2)

par(mar=c(4,4,1,0.5))
plot(-log10(res_chiapet_rep2[[1]]$pval), -log10(res_chiapet[[1]]$pval), col = "#0000FF14", pch = 20, xlab = "With Reps", ylab = "Without Reps")
plot(-log10(res_chiapet_rep2[[2]]$pval), -log10(res_chiapet[[2]]$pval), col = "#0000FF14", pch = 20, xlab = "With Reps", ylab = "Without Reps", main=names(res_chiapet_rep2)[[2]])
plot(-log10(res_chiapet_rep2[[3]]$pval), -log10(res_chiapet[[3]]$pval), col = "#0000FF14", pch = 20, xlab = "With Reps", ylab = "Without Reps", main=names(res_chiapet_rep2)[[3]])
plot(-log10(res_chiapet_rep2[[4]]$pval), -log10(res_chiapet[[4]]$pval), col = "#0000FF14", pch = 20, xlab = "With Reps", ylab = "Without Reps", main=names(res_chiapet_rep2)[[4]])

par(mar=c(0,0,0,0))
plot.new()
text(0.66, 0.66,paste0("cor = ",round(correaltion_chiapet_mer_vs_2rep[[1]],2)),cex=1,font=2)
plot.new()
text(0.66, 0.66,paste0("cor = ",round(correaltion_chiapet_mer_vs_2rep[[2]],2)),cex=1,font=2)
plot.new()
text(0.66, 0.66,paste0("cor = ",round(correaltion_chiapet_mer_vs_2rep[[3]],2)),cex=1,font=2)
plot.new()
text(0.66, 0.66,paste0("cor = ",round(correaltion_chiapet_mer_vs_2rep[[4]],2)),cex=1,font=2)

```

#[HiChIP merged] Differential Tests - statistical power of identifying differential genomic intervals for merged and single replicates
```{r}
#Define the correlation between single and merged replicates
correaltion_hichip_mer_vs_2rep=c()
for (name in names(res_hichip)){
  correaltion_hichip_mer_vs_2rep[[name]]=cor(res_hichip_rep2[[name]]$pval, res_hichip[[name]]$pval, method = "spearman")
}

png(paste0('plots/',experiment,'_correlation_pval_single_merged_wout_reduce_param_all.png'), res = 300, width = 2200, height = 1100)
layout(matrix(c(1,3,7,2,4,8,2,5,9,2,6,10),ncol=4),heights=c(1,3,0.5,1,3,0.5,1,3,0.5,1,3,0.5), widths=c(2, 1.5, 1.5, 1.5))

par(mar=c(0,0,0,0))
plot.new()
text(0.5,0.5,"All trios",cex=1.5,font=2)
plot.new()
text(0.5,0.5,"Within pairs of trios",cex=1.5,font=2)

par(mar=c(4,4,1,0.5))
plot(-log10(res_hichip_rep2[[1]]$pval), -log10(res_hichip[[1]]$pval), col = "#0000FF14", pch = 20, xlab = "With Reps", ylab = "Without Reps")
plot(-log10(res_hichip_rep2[[2]]$pval), -log10(res_hichip[[2]]$pval), col = "#0000FF14", pch = 20, xlab = "With Reps", ylab = 'Without Reps', main=names(res_hichip_rep2)[[2]])
plot(-log10(res_hichip_rep2[[3]]$pval), -log10(res_hichip[[3]]$pval), col = "#0000FF14", pch = 20, xlab = "With Reps", ylab = "Without Reps", main=names(res_hichip_rep2)[[3]])
plot(-log10(res_hichip_rep2[[4]]$pval), -log10(res_hichip[[4]]$pval), col = "#0000FF14", pch = 20, xlab = "With Reps", ylab = "Without Reps", main=names(res_hichip_rep2)[[4]])

par(mar=c(0,0,0,0))
plot.new()
text(0.66, 0.66,paste0("cor = ",round(correaltion_hichip_mer_vs_2rep[[1]],2)),cex=1,font=2)
plot.new()
text(0.66, 0.66,paste0("cor = ",round(correaltion_hichip_mer_vs_2rep[[2]],2)),cex=1,font=2)
plot.new()
text(0.66, 0.66,paste0("cor = ",round(correaltion_hichip_mer_vs_2rep[[3]],2)),cex=1,font=2)
plot.new()
text(0.66, 0.66,paste0("cor = ",round(correaltion_hichip_mer_vs_2rep[[4]],2)),cex=1,font=2)

#[-log10(pval)]

```

#[ChIA-PET merged] Analysis of the results: Show which peaks were filtered by pval based on their mean_value
```{r}
experiment="ChIA-PET"

# Create tables that will include all important information for the analysis
common_chiapet_manorm=list(
  create_table_common_peaks_with_info(norm_chiapet, res_chiapet, conds_chiapet, trios[1:2]),
  create_table_common_peaks_with_info(norm_chiapet, res_chiapet, conds_chiapet,trios[c(1,3)]),
  create_table_common_peaks_with_info(norm_chiapet, res_chiapet, conds_chiapet, trios[2:3]))
names(common_chiapet_manorm)=create_short_name_for_col(trios)

# Create additional tables with lower and higher values of mean values (select the squares)
mean_cutoff=10

common_chiapet_manorm=add_greater_and_lower_mean_ranges_tables(common_chiapet_manorm, mean_cutoff, trios[1:2])
common_chiapet_manorm=add_greater_and_lower_mean_ranges_tables(common_chiapet_manorm, mean_cutoff, trios[c(1,3)])
common_chiapet_manorm=add_greater_and_lower_mean_ranges_tables(common_chiapet_manorm, mean_cutoff, trios[2:3])

# Create tables that will show which mean values have cell lines and their pval

pos_false_tables_chiapet=list(
  create_fp_tables(common_chiapet_manorm[[1]],trios[1:2]),
  create_fp_tables(common_chiapet_manorm[[4]],trios[1:2]),  
  create_fp_tables(common_chiapet_manorm[[5]],trios[1:2]),
  create_fp_tables(common_chiapet_manorm[[2]],trios[c(1,3)]),
  create_fp_tables(common_chiapet_manorm[[6]],trios[c(1,3)]),
  create_fp_tables(common_chiapet_manorm[[7]],trios[c(1,3)]),
  create_fp_tables(common_chiapet_manorm[[3]],trios[2:3]),
  create_fp_tables(common_chiapet_manorm[[8]],trios[2:3]),
  create_fp_tables(common_chiapet_manorm[[9]],trios[2:3]))

names(pos_false_tables_chiapet)=names(common_chiapet_manorm)[c(1,4,5,2,6,7,3,8,9)]

# # Save graphs that will show which mean values have cell lines and their pval
# 
# par="isPval"
# prefix="_mrgRep_tr"
# 
# save_fp_graphs_with_mean_values(pos_false_tables_chiapet,trios[1:2], experiment, paste0("all",prefix),par)
# save_fp_graphs_with_mean_values(pos_false_tables_chiapet,trios[1:2], experiment, paste0("mean>=10",prefix), par)    
# save_fp_graphs_with_mean_values(pos_false_tables_chiapet,trios[1:2], experiment, paste0("mean<10",prefix), par)
# save_fp_graphs_with_mean_values(pos_false_tables_chiapet,trios[c(1,3)], experiment, paste0("all",prefix), par)
# save_fp_graphs_with_mean_values(pos_false_tables_chiapet,trios[c(1,3)], experiment, paste0("mean>=10",prefix), par)
# save_fp_graphs_with_mean_values(pos_false_tables_chiapet,trios[c(1,3)], experiment, paste0("mean<10",prefix), par)
# save_fp_graphs_with_mean_values(pos_false_tables_chiapet,trios[2:3], experiment, paste0("all",prefix), par)
# save_fp_graphs_with_mean_values(pos_false_tables_chiapet,trios[2:3], experiment, paste0("mean>=10",prefix), par)
# save_fp_graphs_with_mean_values(pos_false_tables_chiapet,trios[2:3], experiment, paste0("mean<10",prefix), par)

```

#[HiChIP merged] Analysis of the results: Show which peaks were filtered by pval based on their mean_value
```{r}
experiment="HiChIP"
trios=c("GM19238", "GM19239", "GM19240")

# Create tables that will include all important information for the analysis
common_hichip_manorm=list(
  create_table_common_peaks_with_info(norm_hichip, res_hichip, conds_hichip, trios[1:2]),
  create_table_common_peaks_with_info(norm_hichip, res_hichip, conds_hichip, trios[c(1,3)]),
  create_table_common_peaks_with_info(norm_hichip, res_hichip, conds_hichip, trios[2:3]))
names(common_hichip_manorm)=create_short_name_for_col(trios)

# Create additional tables with lower and higher values of mean values (select the squares)
mean_cutoff=10

common_hichip_manorm=add_greater_and_lower_mean_ranges_tables(common_hichip_manorm, mean_cutoff, trios[1:2])
common_hichip_manorm=add_greater_and_lower_mean_ranges_tables(common_hichip_manorm, mean_cutoff, trios[c(1,3)])
common_hichip_manorm=add_greater_and_lower_mean_ranges_tables(common_hichip_manorm, mean_cutoff, trios[2:3])

# Create tables that will show which mean values have cell lines and their pval
pos_false_tables_hichip=list(
    create_fp_tables(common_hichip_manorm[[1]],trios[1:2]),
  create_fp_tables(common_hichip_manorm[[4]],trios[1:2]),  
  create_fp_tables(common_hichip_manorm[[5]],trios[1:2]),
  create_fp_tables(common_hichip_manorm[[2]],trios[c(1,3)]),
  create_fp_tables(common_hichip_manorm[[6]],trios[c(1,3)]),
  create_fp_tables(common_hichip_manorm[[7]],trios[c(1,3)]),
  create_fp_tables(common_hichip_manorm[[3]],trios[2:3]),
  create_fp_tables(common_hichip_manorm[[8]],trios[2:3]),
  create_fp_tables(common_hichip_manorm[[9]],trios[2:3]))

names(pos_false_tables_hichip)=names(common_hichip_manorm)[c(1,4,5,2,6,7,3,8,9)]

# # Save graphs that will show which mean values have cell lines and their pval
# 
# par="isPval"
# prefix="_mrgRep_tr"
# 
# save_fp_graphs_with_mean_values(pos_false_tables_hichip,trios[1:2], experiment, paste0("all",prefix),par)
# save_fp_graphs_with_mean_values(pos_false_tables_hichip,trios[1:2], experiment, paste0("mean>=10",prefix), par)    
# save_fp_graphs_with_mean_values(pos_false_tables_hichip,trios[1:2], experiment, paste0("mean<10",prefix), par)
# save_fp_graphs_with_mean_values(pos_false_tables_hichip,trios[c(1,3)], experiment, paste0("all",prefix), par)
# save_fp_graphs_with_mean_values(pos_false_tables_hichip,trios[c(1,3)], experiment, paste0("mean>=10",prefix), par)
# save_fp_graphs_with_mean_values(pos_false_tables_hichip,trios[c(1,3)], experiment, paste0("mean<10",prefix), par)
# save_fp_graphs_with_mean_values(pos_false_tables_hichip,trios[2:3], experiment, paste0("all",prefix), par)
# save_fp_graphs_with_mean_values(pos_false_tables_hichip,trios[2:3], experiment, paste0("mean>=10",prefix), par)
# save_fp_graphs_with_mean_values(pos_false_tables_hichip,trios[2:3], experiment, paste0("mean<10",prefix), par)
# rm(prefix)
```

#[ChIA-PET merged] Confusion matrices
```{r}
# List that contains filtered peaks (wout sex chromosomes and peaks that are coming from 3 cell line) 
# They are being used to create confusion matrices
peaks_excl_3_cell_line_and_sex_chr=vector(mode = "list", length = 9)
names(peaks_excl_3_cell_line_and_sex_chr)=names(pos_false_tables_chiapet)

n=cell1=1
cell2=2

for (pair in names(peaks_excl_3_cell_line_and_sex_chr)){
  tmp1=anti_join(common_chiapet_manorm[[pair]], 
                 common_chiapet_manorm[[pair]][common_chiapet_manorm[[pair]]$chrom=="chrX" |
                                               common_chiapet_manorm[[pair]]$chrom=="chrY",])
  tmp1=anti_join(tmp1, tmp1[tmp1[[paste0(trios[cell1],".occupancy")]]==0 & 
                         tmp1[[paste0(trios[cell2],".occupancy")]]==0,])
  n=n+1
  if (n==4){cell2=cell2+1}
  if (n==7){cell1=cell1+1}
  
  peaks_excl_3_cell_line_and_sex_chr[[pair]]=tmp1
  rm(tmp1)
}
rm(cell1, cell2, n, pair)

# Create confusion tables for every pairs of replicates and greater and lower ranges                  
confusion_tables_chiapet=vector(mode="list", length=NROW(peaks_excl_3_cell_line_and_sex_chr))
names(confusion_tables_chiapet)=names(peaks_excl_3_cell_line_and_sex_chr)

for (i in 1:NROW(confusion_tables_chiapet)){
  confusion_tables_chiapet[i]=list(caret::confusionMatrix(factor(peaks_excl_3_cell_line_and_sex_chr[[names(confusion_tables_chiapet)[i]]]$common_pval, levels=c(TRUE, FALSE)), 
                       factor(peaks_excl_3_cell_line_and_sex_chr[[names(confusion_tables_chiapet)[i]]]$predicted_rev, levels=c(TRUE, FALSE)),
                       dnn=c(paste0("pval>",p_value), "SPP_detected")))
}

# Collect data for the ROI curve
if (!exists("ROI_curve")){
  ROI_curve=data.frame()
  ROI_curve[nrow(ROI_curve)+length(confusion_tables_chiapet),]=names(confusion_tables_chiapet)
  row.names(ROI_curve)=names(confusion_tables_chiapet)
}

accuracy=c()
for (pair in names(confusion_tables_chiapet)){
  tmp=confusion_tables_chiapet[[pair]]$overall[[1]]
  accuracy=c(accuracy, tmp)
}

ROI_curve[,ncol(ROI_curve) + 1]=as.data.frame(accuracy)
colnames(ROI_curve)[ncol(ROI_curve)]=paste0("p_value=",toString(p_value))

# Table that are lying under the confusion matrices (TP, TN, FP, FN)
# 4 CASES
confusion_data_chiapet=vector(mode="list", length=3)
names(confusion_data_chiapet)=create_short_name_for_col(trios)

cell1=n=1
cell2=2
for (pair in names(confusion_data_chiapet)){
  confusion_data_chiapet[[pair]]=
    # Both show common (TP)
    list(
      TP=peaks_excl_3_cell_line_and_sex_chr[[pair]][peaks_excl_3_cell_line_and_sex_chr[[pair]]$common_pval==TRUE &
                                                      peaks_excl_3_cell_line_and_sex_chr[[pair]][[paste0(trios[cell1], ".occupancy")]]==1 &
                                                      peaks_excl_3_cell_line_and_sex_chr[[pair]][[paste0(trios[cell2], ".occupancy")]]==1,],
      # Spp shows yes, but pval shows different strength (FP)
      FP=peaks_excl_3_cell_line_and_sex_chr[[pair]][peaks_excl_3_cell_line_and_sex_chr[[pair]]$common_pval==FALSE &
                                                      peaks_excl_3_cell_line_and_sex_chr[[pair]][[paste0(trios[cell1], ".occupancy")]]==1 &
                                                      peaks_excl_3_cell_line_and_sex_chr[[pair]][[paste0(trios[cell2], ".occupancy")]]==1,],
      # SPP shows no, but pval shows, że siła jest taka sama (FN)
      FN=peaks_excl_3_cell_line_and_sex_chr[[pair]][peaks_excl_3_cell_line_and_sex_chr[[pair]]$common_pval==TRUE &
                                                      (peaks_excl_3_cell_line_and_sex_chr[[pair]][[paste0(trios[cell1], ".occupancy")]]==0 |
                                                      peaks_excl_3_cell_line_and_sex_chr[[pair]][[paste0(trios[cell2], ".occupancy")]]==0),],
       # SPP shows no and manorm agrees (TN)
       TN=peaks_excl_3_cell_line_and_sex_chr[[pair]][peaks_excl_3_cell_line_and_sex_chr[[pair]]$common_pval==FALSE &
                                                      (peaks_excl_3_cell_line_and_sex_chr[[pair]][[paste0(trios[cell1], ".occupancy")]]==0 |
                                                      peaks_excl_3_cell_line_and_sex_chr[[pair]][[paste0(trios[cell2], ".occupancy")]]==0),])
    n=n+1
    if(n==2){cell2=cell2+1}
    if(n==3){cell1=cell1+1}
}
rm(cell1, cell2, n, pair)
rm(peaks_excl_3_cell_line_and_sex_chr)

```

#[HiChIP merged] Confusion matrices
```{r}
# List that contains filtered peaks (wout sex chromosomes and peaks that are coming from 3 cell line) 
# They are being used to create confusion matrices
peaks_excl_3_cell_line_and_sex_chr=vector(mode = "list", length = 9)
names(peaks_excl_3_cell_line_and_sex_chr)=names(pos_false_tables_hichip)

n=cell1=1
cell2=2

for (pair in names(peaks_excl_3_cell_line_and_sex_chr)){
  tmp1=anti_join(common_hichip_manorm[[pair]], 
                 common_hichip_manorm[[pair]][common_hichip_manorm[[pair]]$chrom=="chrX" |
                                               common_hichip_manorm[[pair]]$chrom=="chrY",])
  tmp1=anti_join(tmp1, tmp1[tmp1[[paste0(trios[cell1],".occupancy")]]==0 & 
                         tmp1[[paste0(trios[cell2],".occupancy")]]==0,])
  n=n+1
  if (n==4){cell2=cell2+1}
  if (n==7){cell1=cell1+1}
  
  peaks_excl_3_cell_line_and_sex_chr[[pair]]=tmp1
  rm(tmp1)
}
rm(cell1, cell2, n, pair)

# Create confusion tables for every pairs of replicates and greater and lower ranges                  
confusion_tables_hichip=vector(mode="list", length=NROW(peaks_excl_3_cell_line_and_sex_chr))
names(confusion_tables_hichip)=names(peaks_excl_3_cell_line_and_sex_chr)

for (i in 1:NROW(confusion_tables_hichip)){
  confusion_tables_hichip[i]=list(caret::confusionMatrix(factor(peaks_excl_3_cell_line_and_sex_chr[[names(confusion_tables_hichip)[i]]]$common_pval, levels=c(TRUE, FALSE)), 
                       factor(peaks_excl_3_cell_line_and_sex_chr[[names(confusion_tables_hichip)[i]]]$predicted_rev, levels=c(TRUE, FALSE)),
                       dnn=c(paste0("pval>",p_value), "SPP_detected")))
}

# Collect data for the ROI curve
if (!exists("ROI_curve_hichip")){
  ROI_curve_hichip=data.frame()
  ROI_curve_hichip[nrow(ROI_curve_hichip)+length(confusion_tables_chiapet),]=names(confusion_tables_chiapet)
  row.names(ROI_curve_hichip)=names(confusion_tables_chiapet)
}

accuracy=c()
for (pair in names(confusion_tables_chiapet)){
  tmp=confusion_tables_chiapet[[pair]]$overall[[1]]
  accuracy=c(accuracy, tmp)
}

ROI_curve_hichip[,ncol(ROI_curve_hichip) + 1]=as.data.frame(accuracy)
colnames(ROI_curve_hichip)[ncol(ROI_curve_hichip)]=paste0("p_value=",toString(p_value))

# Table that are lying under the confusion matrices (TP, TN, FP, FN)
# 4 CASES
confusion_data_hichip=vector(mode="list", length=3)
names(confusion_data_hichip)=create_short_name_for_col(trios)

cell1=n=1
cell2=2
for (pair in names(confusion_data_hichip)){
  confusion_data_hichip[[pair]]=
    # Both show common (TP)
    list(
      TP=peaks_excl_3_cell_line_and_sex_chr[[pair]][peaks_excl_3_cell_line_and_sex_chr[[pair]]$common_pval==TRUE &
                                                      peaks_excl_3_cell_line_and_sex_chr[[pair]][[paste0(trios[cell1], ".occupancy")]]==1 &
                                                      peaks_excl_3_cell_line_and_sex_chr[[pair]][[paste0(trios[cell2], ".occupancy")]]==1,],
      # Spp shows yes, but pval shows different strength (FP)
      FP=peaks_excl_3_cell_line_and_sex_chr[[pair]][peaks_excl_3_cell_line_and_sex_chr[[pair]]$common_pval==FALSE &
                                                      peaks_excl_3_cell_line_and_sex_chr[[pair]][[paste0(trios[cell1], ".occupancy")]]==1 &
                                                      peaks_excl_3_cell_line_and_sex_chr[[pair]][[paste0(trios[cell2], ".occupancy")]]==1,],
      # SPP shows no, but pval shows, że siła jest taka sama (FN)
      FN=peaks_excl_3_cell_line_and_sex_chr[[pair]][peaks_excl_3_cell_line_and_sex_chr[[pair]]$common_pval==TRUE &
                                                      (peaks_excl_3_cell_line_and_sex_chr[[pair]][[paste0(trios[cell1], ".occupancy")]]==0 |
                                                      peaks_excl_3_cell_line_and_sex_chr[[pair]][[paste0(trios[cell2], ".occupancy")]]==0),],
       # SPP shows no and manorm agrees (TN)
       TN=peaks_excl_3_cell_line_and_sex_chr[[pair]][peaks_excl_3_cell_line_and_sex_chr[[pair]]$common_pval==FALSE &
                                                      (peaks_excl_3_cell_line_and_sex_chr[[pair]][[paste0(trios[cell1], ".occupancy")]]==0 |
                                                      peaks_excl_3_cell_line_and_sex_chr[[pair]][[paste0(trios[cell2], ".occupancy")]]==0),])
    n=n+1
    if(n==2){cell2=cell2+1}
    if(n==3){cell1=cell1+1}
}
rm(cell1, cell2, n, pair)
rm(peaks_excl_3_cell_line_and_sex_chr)

```

#[ChIA-PET merged] Select possible constant peaks
```{r}
confusion_data=confusion_data_chiapet

chiapet_fn_ids=list(
  
  ### PAIRS of cell lines ###
  
  # Probable constant peaks are those, in which peaks for 2 cell lines are TP, and for the third line FN
  # For examples, if GM38_GM39 are TP (by SPP and pval) and GM38_GM40 are negative (by SPP), 
  # but positive by pval (>(0.05)) than those peaks are considered to be constant
  
# Results
  # Between 38_39 and 40 --> + 3510
  # Between 38_40 and 39 --> + 2362
  # Between 39_40 and 38 --> + 3805
  
  fn_38_39=intersect(
    confusion_data$GM38_GM39$TP$norm.index,
    unique(confusion_data$GM38_GM40$FN[confusion_data$GM38_GM40$FN$GM19240.occupancy==FALSE,]$norm.index,
           confusion_data$GM39_GM40$FN[confusion_data$GM39_GM40$FN$GM19240.occupancy==FALSE,]$norm.index)),
  fn_38_40=intersect(
    confusion_data$GM38_GM40$TP$norm.index,
    unique(confusion_data$GM38_GM39$FN[confusion_data$GM38_GM39$FN$GM19239.occupancy==FALSE,]$norm.index,
           confusion_data$GM39_GM40$FN[confusion_data$GM39_GM40$FN$GM19239.occupancy==FALSE,]$norm.index)),
  fn_39_40=intersect(
    confusion_data$GM39_GM40$TP$norm.index,
    unique(confusion_data$GM38_GM39$FN[confusion_data$GM38_GM39$FN$GM19238.occupancy==FALSE,]$norm.index,
           confusion_data$GM38_GM40$FN[confusion_data$GM38_GM40$FN$GM19238.occupancy==FALSE,]$norm.index)),
  
  ### SINGLE CELL LINE ###
  
  # Peaks were 
  
  # Probable constant peaks are those, in which peaks for 2 cell lines are TP, and for the third line FN
  # For examples, if GM38_GM39 are TP (by SPP and pval) and GM38_GM40 are negative (by SPP), 
  # but positive by pval (>(0.05)) than those peaks are considered to be constant
  
# Results
  # Between 38 and other cell_lines --> 8647 vs 9996 >> 6077 common
  # Between 39 and other cell_lines --> 7773 vs 6897 >> 3548 common
  # Between 40 and other cell_lines --> 4770 vs 3701 >> 1174 common
  
  fn_38=intersect(
    confusion_data$GM38_GM39$FN[confusion_data$GM38_GM39$FN$GM19238.occupancy==TRUE,]$norm.index,
    confusion_data$GM38_GM40$FN[confusion_data$GM38_GM40$FN$GM19238.occupancy==TRUE,]$norm.index),

  fn_39=intersect(
    confusion_data$GM38_GM39$FN[confusion_data$GM38_GM39$FN$GM19239.occupancy==TRUE,]$norm.index,
    confusion_data$GM39_GM40$FN[confusion_data$GM39_GM40$FN$GM19239.occupancy==TRUE,]$norm.index),

  fn_40=intersect(
    confusion_data$GM38_GM40$FN[confusion_data$GM38_GM40$FN$GM19240.occupancy==TRUE,]$norm.index,
    confusion_data$GM39_GM40$FN[confusion_data$GM39_GM40$FN$GM19240.occupancy==TRUE,]$norm.index))

### Deduplicate the peaks
# 5772 peaks are constant and were supposed to be unique for PAIRS of cell lines
# with pval=0.03 --> 6047
# with pval=0.06 --> 5620
id_constant_chiapet_by_manorm_peaks_pairs=unique(unlist(chiapet_fn_ids[1:3]))
# 8933 peaks are constant and were supposed to be unique for cell lines
# with pval=0.03 --> 9472
# with pval=0.06 --> 8664
id_constant_chiapet_by_manorm_peaks_single_lines=unique(unlist(chiapet_fn_ids[4:6]))

# Get peaks using their indexes
# 14705 of possible unique peaks
# with pval=0.03 --> 15519 
# with pval=0.06 --> 14284 
constant_chiapet_by_manorm_peaks=norm_chiapet[sort(c(id_constant_chiapet_by_manorm_peaks_pairs, 
                                              id_constant_chiapet_by_manorm_peaks_single_lines)),]

constant_chiapet_by_manorm_peaks.gr=sort(GRanges(constant_chiapet_by_manorm_peaks))

### Overlapping pf the peaks
# 9218 of 13811 are overlaping with ChIP-Seq constant peaks (0.667439)
# with pval=0.03 --> 9715 of 14524 (0.6688929)
# with pval=0.06 --> 8947 of 13447 (0.6653529) !!
NROW(subsetByOverlaps(IRanges::reduce(constant_chiapet_by_manorm_peaks.gr+p_exp), IRanges::reduce(common_peaks_for_trios_ChIPSeq$constant_peaks+p_exp)))
NROW(IRanges::reduce(constant_chiapet_by_manorm_peaks.gr+p_exp))

# 0 of 14705 are actually overlaping with SPP detected peaks, 
# but for some reason had false occupancy (some of them are narrow)
subsetByOverlaps(constant_chiapet_by_manorm_peaks.gr, common_peaks_for_trios_ChIAPET$constant_peaks) #(chyba bez motywu tez tu sa)

# That's why we want to reduce these peaks. In total we have 39031 (19333+19698) peaks, 
# after reduction 39153 
# with pval=0.03 --> 39967
# with pval=0.06 --> 38732
chiapet_constant_peaks_with_manorm=IRanges::reduce(c(constant_chiapet_by_manorm_peaks.gr, common_peaks_for_trios_ChIAPET$constant_peaks))

# How many initial peaks from ChIA-PET are overlapping with ChIP-Seq constant peaks
# 21981 of 22818 (0.9633184)
subsetByOverlaps(IRanges::reduce(common_peaks_for_trios_ChIAPET$constant_peaks+p_exp), IRanges::reduce(common_peaks_for_trios_ChIPSeq$constant_peaks+p_exp))

# Let's do the overlap of all true peaks with ChIP-Seq constant peaks
# 27960 from 32901 were overlapped (before only 23037, so +6994 new peaks), ChIP-Seq has 37332 peaks. (0.8498222)
# with pval=0.03 --> 28310 from 33453 (0.8462619)
# with pval=0.06 --> 27786 from 32642 (0.8512346)
NROW(subsetByOverlaps(IRanges::reduce(chiapet_constant_peaks_with_manorm+p_exp), IRanges::reduce(common_peaks_for_trios_ChIPSeq$constant_peaks+p_exp)))
NROW(IRanges::reduce(chiapet_constant_peaks_with_manorm+p_exp))

# Check which new peaks were being  ADDITIONALY detected by manorm
subsetByOverlaps(chiapet_constant_peaks_with_manorm, common_peaks_for_trios_ChIAPET$constant_peaks, invert=TRUE)

```

# [HiChIP merged] Select possible constant peaks
```{r}

pos_false_table=pos_false_tables_hichip

### Were unique for pairs of cell lines
# Between 38_39 and 40 --> + 1017
# Between 38_40 and 39 --> + 2377
# Between 39_40 and 38 --> + 722

hichip_fn_ids=list(
  fn_38_39=intersect(
  row.names(pos_false_table[[1]][[1]]),
  unique(row.names(pos_false_table[[4]][[4]][pos_false_table[[4]][[4]]$common_pval==TRUE,]),
              row.names(pos_false_table[[7]][[4]][pos_false_table[[7]][[4]]$common_pval==TRUE,]))),
  fn_38_40=intersect(
  row.names(pos_false_table[[4]][[1]]),
  unique(row.names(pos_false_table[[1]][[4]][pos_false_table[[1]][[4]]$common_pval==TRUE,]),
              row.names(pos_false_table[[7]][[5]][pos_false_table[[7]][[5]]$common_pval==TRUE,]))),
  
  fn_39_40=intersect(
  row.names(pos_false_table[[7]][[1]]),
  unique(row.names(pos_false_table[[1]][[5]][pos_false_table[[1]][[5]]$common_pval==TRUE,]),
              row.names(pos_false_table[[4]][[5]][pos_false_table[[4]][[5]]$common_pval==TRUE,]))),
  
### Were unique for each cell_line
# Between 38 and other cell_lines --> 4266 vs 2911 >> 1729 common
# Between 39 and other cell_lines --> 1136 vs 1450 >> 375 common
# Between 40 and other cell_lines --> 4041 vs 5912 >> 3253 common
  
  fn_38=intersect(
    row.names(pos_false_table[[1]]$false_peaks[pos_false_table[[1]]$false_peaks$common_pval==TRUE &                                           
                                               pos_false_table[[1]]$false_peaks[[paste0(trios[[1]],".occupancy")]]==TRUE & 
                                               pos_false_table[[1]]$false_peaks[[paste0(trios[[2]],".occupancy")]]==FALSE ,]),
    row.names(pos_false_table[[4]]$false_peaks[pos_false_table[[4]]$false_peaks$common_pval==TRUE &                                               
                                               pos_false_table[[4]]$false_peaks[[paste0(trios[[1]],".occupancy")]]==TRUE &
                                               pos_false_table[[4]]$false_peaks[[paste0(trios[[3]],".occupancy")]]==FALSE,])),
  fn_39=intersect(
    row.names(pos_false_table[[1]]$false_peaks[pos_false_table[[1]]$false_peaks$common_pval==TRUE &                                             
                                               pos_false_table[[1]]$false_peaks[[paste0(trios[[1]],".occupancy")]]==FALSE &
                                               pos_false_table[[1]]$false_peaks[[paste0(trios[[2]],".occupancy")]]==TRUE,]),
    row.names(pos_false_table[[7]]$false_peaks[pos_false_table[[7]]$false_peaks$common_pval==TRUE &                                                
                                               pos_false_table[[7]]$false_peaks[[paste0(trios[[2]],".occupancy")]]==TRUE &
                                               pos_false_table[[7]]$false_peaks[[paste0(trios[[3]],".occupancy")]]==FALSE,])),
  fn_40=intersect(
    row.names(pos_false_table[[4]]$false_peaks[pos_false_table[[4]]$false_peaks$common_pval==TRUE &                                              
                                               pos_false_table[[4]]$false_peaks[[paste0(trios[[1]],".occupancy")]]==FALSE & 
                                               pos_false_table[[4]]$false_peaks[[paste0(trios[[3]],".occupancy")]]==TRUE,]),
    row.names(pos_false_table[[7]]$false_peaks[pos_false_table[[7]]$false_peaks$common_pval==TRUE &                                                
                                               pos_false_table[[7]]$false_peaks[[paste0(trios[[2]],".occupancy")]]==FALSE & 
                                               pos_false_table[[7]]$false_peaks[[paste0(trios[[3]],".occupancy")]]==TRUE,])))

### Duplicate the peaks
# 4116 peaks are constant and were supposed to be unique for PAIRS of cell lines
id_constant_hichip_by_manorm_peaks_pairs=unique(unlist(hichip_fn_ids[1:3]))
# 5357 peaks are constant and were supposed to be unique for cell lines
id_constant_hichip_by_manorm_peaks_single_lines=unique(unlist(hichip_fn_ids[4:6]))

constant_hichip_by_manorm_peaks=norm_hichip[c(id_constant_hichip_by_manorm_peaks_pairs, 
                                              id_constant_hichip_by_manorm_peaks_single_lines),]

# constant_hichip_by_manorm_peaks$by_spp=FALSE
# constant_hichip_by_manorm_peaks$by_manorm=TRUE

constant_hichip_by_manorm_peaks.gr=sort(GRanges(constant_hichip_by_manorm_peaks))

### Overlap of the peaks
# 4763 of 9473 are overlaping with ChIP-Seq
NROW(subsetByOverlaps(IRanges::reduce(constant_hichip_by_manorm_peaks.gr+p_exp), IRanges::reduce(common_peaks_for_trios_ChIPSeq$constant_peaks+p_exp)))
NROW(IRanges::reduce(constant_hichip_by_manorm_peaks.gr+p_exp))

# 1075 of 9473 are actually overlaping with SPP detected peaks, but for some reason had false occupancy
subsetByOverlaps(constant_hichip_by_manorm_peaks.gr, common_peaks_for_trios_HiChIP$constant_peaks)

# That's why we want to reduce these peaks. In total we have 30677 peaks, after reduction 29600 (2 more peaks were detected as overlapped)
hichip_constant_peaks_with_manorm=IRanges::reduce(c(constant_hichip_by_manorm_peaks.gr, common_peaks_for_trios_HiChIP$constant_peaks))

# How many initial peaks from HiChIP are overlapping with ChIP-Seq constant peaks
# 21981 of 22818 (0.9633184)
subsetByOverlaps(IRanges::reduce(common_peaks_for_trios_HiChIP$constant_peaks+p_exp),
                 IRanges::reduce(common_peaks_for_trios_ChIPSeq$constant_peaks+p_exp))

# Let's do the overlap of all true peaks with ChIP-Seq constant peaks
# 27960 from 32901 were overlapped (before only 23037, so +6994 new peaks), ChIP-Seq has 37332 peaks. (0.8498222)
# with pval=0.03 --> 28310 from 33453 (0.8462619)
# with pval=0.06 --> 27786 from 32642 (0.8512346)
NROW(subsetByOverlaps(IRanges::reduce(hichip_constant_peaks_with_manorm+p_exp),
                      IRanges::reduce(common_peaks_for_trios_ChIPSeq$constant_peaks+p_exp)))
NROW(IRanges::reduce(hichip_constant_peaks_with_manorm+p_exp))

# Check which new peaks were being  ADDITIONALY detected by manorm
subsetByOverlaps(hichip_constant_peaks_with_manorm, common_peaks_for_trios_HiChIP$constant_peaks, invert=TRUE)


```
