---
title: "Peaks comparison of ChIA-PET and HiChIP technologies"
---
"
In this script there are main techniques for comparison of the ChIA-PET and Hi-ChIP data.
All the important functions could be found in "functions_ChIA-PET_HiChIP_YRB.R" script
Output plots are saved under project_dir/plots
"
--- 

"
Script is assuming that there are 3 folders inside of the project directory: "chiapet", "hichip" and "chipseq"
Inside of each directory there is a folder, that contain the run names, ec. GM19238, GM19238_rep1 
Althought data could be also provided with direct links.
"

# Update the functions if they are changed
```{r}
upd_functions=function(){
  source("functions_ChIA-PET_HiChIP_YRB.R")
}
```

# Read CTCF motif file
```{r}
# Read CTCF motif peaks
CTCF.hg38 = read.table(file.path("data/CTCF_hg38.txt"))
CTCF.hg38 = GRanges(seqnames = CTCF.hg38$V1, 
                    IRanges(start = CTCF.hg38$V3, 
                            width = CTCF.hg38$V4), 
                    strand = ifelse(CTCF.hg38$V5=='p', "+", "-"), 
                    score=CTCF.hg38$V6)
CTCF.hg38 = CTCF.hg38[CTCF.hg38$score >0]
```

# [Merged replicates] Upload of the peaks data
```{r}
trios=c("GM19238", "GM19239", "GM19240")

experiment_1<<-"chiapet"
experiment_2<<-"hichip"
experiment_3<<-"chipseq"

#peaks_extension
p_exp<<-1000

peaks_raw_ChIAPET=GRangesList("GM19238"=GRanges(), "GM19239"=GRanges(), "GM19240"=GRanges())
peaks_raw_HiChIP=GRangesList("GM19238"=GRanges(), "GM19239"=GRanges(), "GM19240"=GRanges())
peaks_raw_ChIPSeq=GRangesList("GM19238"=GRanges(), "GM19239"=GRanges(), "GM19240"=GRanges())

peaks_wout_sex_chr_reduced_ChIAPET=peaks_wout_sex_chr_ChIAPET=peaks_with_motif_ChIAPET=peaks_reduced_with_motif_ChIAPET=peaks_raw_ChIAPET
peaks_wout_sex_chr_reduced_HiChIP=peaks_wout_sex_chr_HiChIP=peaks_with_motif_HiChIP=peaks_reduced_with_motif_HiChIP=peaks_raw_HiChIP
peaks_wout_sex_chr_reduced_ChIPSeq=peaks_wout_sex_chr_ChIPSeq=peaks_with_motif_ChIPSeq=peaks_reduced_with_motif_ChIPSeq=peaks_raw_ChIPSeq

#Create GRangesLists that will conclude all the trios data

for (cell_line in trios){
  
  peaks_raw_ChIAPET[[cell_line]]=read_peaks(get_peaks_path(experiment_1, cell_line))
  peaks_raw_HiChIP[[cell_line]]=read_peaks(get_peaks_path(experiment_2, cell_line))
  peaks_raw_ChIPSeq[[cell_line]]=read_peaks(get_peaks_path(experiment_3, cell_line))
  
  peaks_with_motif_ChIAPET[[cell_line]]=peaks_raw_ChIAPET[[cell_line]][unique(queryHits(findOverlaps(peaks_raw_ChIAPET[[cell_line]], CTCF.hg38)))]
  peaks_with_motif_HiChIP[[cell_line]]=peaks_raw_HiChIP[[cell_line]][unique(queryHits(findOverlaps(peaks_raw_HiChIP[[cell_line]], CTCF.hg38)))]
  peaks_with_motif_ChIPSeq[[cell_line]]=peaks_raw_ChIPSeq[[cell_line]][unique(queryHits(findOverlaps(peaks_raw_ChIPSeq[[cell_line]], CTCF.hg38)))]
  
  peaks_reduced_with_motif_ChIAPET[[cell_line]]=IRanges::reduce(peaks_with_motif_ChIAPET[[cell_line]]+p_exp)
  peaks_reduced_with_motif_HiChIP[[cell_line]]=IRanges::reduce(peaks_with_motif_HiChIP[[cell_line]]+p_exp)
  peaks_reduced_with_motif_ChIPSeq[[cell_line]]=IRanges::reduce(peaks_with_motif_ChIPSeq[[cell_line]]+p_exp)
  
  peaks_wout_sex_chr_ChIAPET[[cell_line]]=subset(
    peaks_with_motif_ChIAPET[[cell_line]],
    !(peaks_with_motif_ChIAPET[[cell_line]]@seqnames %in% c('chrY', 'chrX', 'chrM')))
  peaks_wout_sex_chr_HiChIP[[cell_line]]=subset(
    peaks_with_motif_HiChIP[[cell_line]],
    !(peaks_with_motif_HiChIP[[cell_line]]@seqnames %in% c('chrY', 'chrX', 'chrM')))
  peaks_wout_sex_chr_ChIPSeq[[cell_line]]=subset(
    peaks_with_motif_ChIPSeq[[cell_line]],
    !(peaks_with_motif_ChIPSeq[[cell_line]]@seqnames %in% c('chrY', 'chrX', 'chrM')))
  
  peaks_wout_sex_chr_reduced_ChIAPET[[cell_line]]=subset(
    peaks_reduced_with_motif_ChIAPET[[cell_line]],
    !(peaks_reduced_with_motif_ChIAPET[[cell_line]]@seqnames %in% c('chrY', 'chrX', 'chrM')))
  peaks_wout_sex_chr_reduced_HiChIP[[cell_line]]=subset(
    peaks_reduced_with_motif_HiChIP[[cell_line]],
    !(peaks_reduced_with_motif_HiChIP[[cell_line]]@seqnames %in% c('chrY', 'chrX', 'chrM')))
  peaks_wout_sex_chr_reduced_ChIPSeq[[cell_line]]=subset(
    peaks_reduced_with_motif_ChIPSeq[[cell_line]],
    !(peaks_reduced_with_motif_ChIPSeq[[cell_line]]@seqnames %in% c('chrY', 'chrX', 'chrM')))
}

```

# Comparison of peaks between single and merged replicates
```{r}

# ChIA-PET
experiment<<-"chiapet"
common=find_true_all_relative_overlaps(IRanges::reduce(rep2_peaks_with_motif_ChIAPET$GM19239_rep1+1000), 
                                    IRanges::reduce(rep2_peaks_with_motif_ChIAPET$GM19239_rep2+1000), 
                                    IRanges::reduce(peaks_with_motif_ChIAPET$GM19239+1000),
                                    "replicates")
areas=define_subsets_for_3_venn_from_common(common)
png(paste0('plots/venn_diagrams/Common_raw_peaks_ChIA-PET_', cell_line, '_different_replicates_3.png'), res = 300, width = 4200, height = 4200)
plot.new()                                             

VennDiagram::draw.triple.venn(areas$area1, areas$area2, areas$area3, 
                                           areas$n12, areas$n23, areas$n13, areas$n123,
                     fill=c(color("GM19239_rep1"), color("GM19239_rep2"), color(experiment)),
                     category=c("GM19239_rep1", "GM19239_rep2", "GM19239_merged"),
                     print.mode=c('raw', 'percent'),
                     lwd = 4,
                     cat.dist = c(0.06, 0.06, 0.03),
                     cat.cex = 3, 
                     margin = 0.12,
                     cex = 3)
rm(common, areas)

# hichip
experiment<<-"hichip"
common=find_true_all_relative_overlaps(IRanges::reduce(rep2_peaks_with_motif_HiChIP$GM19239_rep1+1000), 
                                    IRanges::reduce(rep2_peaks_with_motif_HiChIP$GM19239_rep2+1000), 
                                    IRanges::reduce(peaks_with_motif_HiChIP$GM19239+1000),
                                    "replicates")
areas=define_subsets_for_3_venn_from_common(common)
png(paste0('plots/venn_diagrams/Common_raw_peaks_Hi-ChIP_', cell_line, '_different_replicates_3.png'), res = 300, width = 4200, height = 4200)
plot.new()                                             

VennDiagram::draw.triple.venn(areas$area1, areas$area2, areas$area3, 
                                           areas$n12, areas$n23, areas$n13, areas$n123,
                     fill=c(color("GM19239_rep1"), color("GM19239_rep2"), color(experiment)),
                     category=c("GM19239_rep1", "GM19239_rep2", "GM19239_merged"),
                     print.mode=c('raw', 'percent'),
                     lwd = 4,
                     cat.dist = c(0.06, 0.06, 0.03),
                     cat.cex = 3, 
                     margin = 0.12,
                     cex = 3)
rm(common, areas)
```

# Peaks comparison inside of the cell line for every technology(x3) (ec. GM19238 --> ChIAPET, HiChIP and ChIPSeq)
```{r}
trios=c("GM19238", "GM19239", "GM19240")

experiment_1<<-"chiapet"
experiment_2<<-"hichip"
experiment_3<<-"chipseq"

for (cell_line in trios){
  
  common_peaks=find_true_all_relative_overlaps(peaks_with_motif_ChIAPET[[cell_line]], 
                                               peaks_with_motif_HiChIP[[cell_line]], 
                                               peaks_with_motif_ChIPSeq[[cell_line]],
                                               "experiments")
  assign(paste0(cell_line, "_common_peaks_3_tech"), common_peaks)
  
  # Draw and save the plots
  png(paste0('plots/venn_diagrams/Common_peaks_between_technologies_', cell_line, '.png'), res = 300, width = 4200, height = 4200)
  plot.new()
  draw_3_venn_diagram(common_peaks)
  dev.off()
  
  # Pairwise Venn diagrams

  png(paste0('plots/venn_diagrams/Common_peaks_between_',experiment_1,'_and_',experiment_2,'_',cell_line,'.png'),
      res = 300, width = 2400, height = 2400)
  plot.new()
  draw_2_venn_diagram(common_peaks, 12)
  dev.off()

  png(paste0('plots/venn_diagrams/Common_peaks_between_',experiment_1,'_and_',experiment_3,'_',cell_line,'.png'),
      res = 300, width = 2400, height = 2400)
  plot.new()
  draw_2_venn_diagram(common_peaks, 13)
  dev.off()

  png(paste0('plots/venn_diagrams/Common_peaks_between_',experiment_2,'_and_',experiment_3,'_',cell_line,'.png'),
      res = 300, width = 2400, height = 2400)
  plot.new()
  draw_2_venn_diagram(common_peaks, 23)
  dev.off()
}

rm(common_peaks)
```

# Reduced peaks comparison inside the cell line for 3 technologies (ec. GM19238 --> ChIAPET, HiChIP and ChIPSeq)
```{r}

trios=c("GM19238", "GM19239", "GM19240")

experiment_1<<-"chiapet"
experiment_2<<-"hichip"
experiment_3<<-"chipseq"

for (cell_line in trios){
  
  common_peaks=find_true_all_relative_overlaps(peaks_reduced_with_motif_ChIAPET[[cell_line]], 
                                               peaks_reduced_with_motif_HiChIP[[cell_line]], 
                                               peaks_reduced_with_motif_ChIPSeq[[cell_line]],
                                               "experiments")
  assign(paste0(cell_line, "_common_peaks_3_tech_red"), common_peaks)
  
  # Draw and save the plots
  png(paste0('plots/venn_diagrams/Common_peaks_between_technologies_', cell_line, '_reduced.png'), res = 300, width = 4200, height = 4200)
  plot.new()
  draw_3_venn_diagram(common_peaks)
  dev.off()
  
  # Pairwise Venn diagrams

  png(paste0('plots/venn_diagrams/Common_peaks_between_',experiment_1,'_and_',experiment_2,'_',cell_line,'_reduced.png'),
      res = 300, width = 2400, height = 2400)
  plot.new()
  draw_2_venn_diagram(common_peaks, 12)
  dev.off()

  png(paste0('plots/venn_diagrams/Common_peaks_between_',experiment_1,'_and_',experiment_3,'_',cell_line,'_reduced.png'),
      res = 300, width = 2400, height = 2400)
  plot.new()
  draw_2_venn_diagram(common_peaks, 13)
  dev.off()

  png(paste0('plots/venn_diagrams/Common_peaks_between_',experiment_2,'_and_',experiment_3,'_',cell_line,'_reduced.png'),
      res = 300, width = 2400, height = 2400)
  plot.new()
  draw_2_venn_diagram(common_peaks, 23)
  dev.off()
}

rm(common_peaks)

```

# Strength of CTCF motif
```{r}
trios=c("GM19238", "GM19239", "GM19240")

#Create GRangesLists that will conclude peaks with CTCF strength info

for (cell_line in trios){
  
  ctcf_strength=GRangesList(GRanges(),GRanges(),GRanges(),GRanges(),GRanges(),GRanges(),GRanges())
  names(ctcf_strength)=names(GM19238_common_peaks_3_tech)
  
  for (overlap in names(ctcf_strength)){
  
    ctcf_strength[[overlap]]=add_motif_info_to_peaks(get(paste0(cell_line,"_common_peaks_3_tech_red"))[[overlap]], CTCF.hg38)
    assign(paste0("ctcf_strength_", cell_line), ctcf_strength)
  }
}
rm(ctcf_strength)

# Calculate the mean max CTCF motif strength
tmp=vector(mode="list", length=NROW(ctcf_strength_GM19238))
names(tmp)=names(ctcf_strength_GM19238)
avergae_max_ctcf=list(tmp,tmp,tmp)
names(avergae_max_ctcf)=trios
rm(tmp)

for (cell_line in trios){
  for (overlap in names(ctcf_strength_GM19238)){
    avergae_max_ctcf[[cell_line]][[overlap]]=mean(get(paste0("ctcf_strength_", cell_line))[[overlap]]$max_motif_CTCF)
  }
}

```

# Histograms CTCF motif
```{r}
png(paste0('plots/peaks/CTCF_motif_strength_GM19238.png'), res = 300, width = 8000, height = 4200)
plot.new()
par(
  mfrow=c(3,3),
  mar=c(5,5,5,5)
)
line<-par(lwd=5)

hist(ctcf_strength_GM19238[[5]]$max_motif_CTCF,
     col="#9496ff", main="Unique peaks in ChIA-PET", 
     xlab="Strongest CTCF motif score", 
     cex.lab=2.5, cex.axis=2.5, cex.main=4)
hist(ctcf_strength_GM19238[[2]]$max_motif_CTCF, 
     col="#73cb91", main="Common peaks ChIA-PET & HiChIP", 
     xlab="Strongest CTCF motif score", 
     cex.lab=2.5, cex.axis=2.5, cex.main=4)
hist(ctcf_strength_GM19238[[6]]$max_motif_CTCF, 
      col="#b1fe88", main="Unique peaks in HiChIP", 
     xlab="Strongest CTCF motif score", 
     cex.lab=2.5, cex.axis=2.5, cex.main=4)
hist(ctcf_strength_GM19238[[3]]$max_motif_CTCF,
      col="#db4e97", main="Common peaks ChIP-Seq & ChIA-PET", 
     xlab="Strongest CTCF motif score", 
     cex.lab=2.5, cex.axis=2.5, cex.main=4)
hist(ctcf_strength_GM19238[[1]]$max_motif_CTCF,
      col="#d36f4f", main="Common peaks for 3 technologies", 
     xlab="Strongest CTCF motif score", 
     cex.lab=2.5, cex.axis=2.5, cex.main=4)
hist(ctcf_strength_GM19238[[4]]$max_motif_CTCF,
      col="#ed8f48", main="Common peaks ChIP-Seq & HiChIP", 
     xlab="Strongest CTCF motif score", 
     cex.lab=2.5, cex.axis=2.5, cex.main=4)
plot.new()
hist(ctcf_strength_GM19238[[7]]$max_motif_CTCF,
col="#ff8f92", main="Unique peaks in ChIP-Seq", 
xlab="Strongest CTCF motif score", 
cex.lab=2.5, cex.axis=2.5, cex.main=4)

dev.off()

```

# Violin plots of CTCF motif
```{r}
# Orders of overlaps from from names(ctcf_strength_GM19238)
ord_of_overlaps=c(5,2,6,7,3,4,1)

# final Boxplots names
names_box_plot <- c(paste("\nCommon \npeaks\n for 3 technologies"), 
                    paste("\nCommon \npeaks\nChIA-PET & \nHiChIP"), 
                    paste("\nCommon \npeaks\n ChIP-Seq & \nChIA-PET"), 
                    paste("\nCommon \npeaks\n ChIP-Seq & \nHiChIP"), 
                    paste("\nUnique \npeaks\n ChIA-PET"), 
                    paste("\nUnique \npeaks\n HiChIP"), 
                    paste("\nUnique \npeaks\n ChIP-Seq")) 

colors=c("#d36f4f","#73cb91", "#db4e97","#ed8f48", "#9496ff","#b1fe88", "#ff8f92")

for (cell_line in trios){
  png(paste0("plots/peaks/CTCF_motif_strength_", cell_line,"_violin.png"), res = 300, width = 5000, height = 3000)
  plot.new()
  
  ctcf_strength_max_motif=data.frame()
  for (overlap in names(ctcf_strength_GM19238)[ord_of_overlaps]){
    tmp_ctcf_df=data.frame(value=get(paste0("ctcf_strength_", cell_line))[[overlap]]$max_motif_CTCF, variable=overlap)
    ctcf_strength_max_motif=rbind(ctcf_strength_max_motif,tmp_ctcf_df)
  }
  rm(tmp_ctcf_df)
  ctcf_strength_max_motif=ctcf_strength_max_motif%>%
    mutate(variable=factor(variable,levels=names(get(paste0("ctcf_strength_", cell_line)))[ord_of_overlaps]))
  
  print(ggplot(ctcf_strength_max_motif, aes(x=variable, y=value, fill=variable))+  
  geom_violin()+
  geom_boxplot(width=0.1)+
  theme_minimal()+
  scale_x_discrete(labels=names_box_plot[ord_of_overlaps])+
  theme(text = element_text(size=25),
        axis.text.x = element_text(angle=0, hjust=0.5))+
  scale_fill_manual(values=colors[ord_of_overlaps])+
  theme(legend.position="none")+
  ylab("CTCF motif score")+
  xlab(c()))
  
  dev.off()
  
}

```

# Add coverage to every peak
```{r}
# trios=c("GM19238", "GM19239", "GM19240")

experiment="chiapet"
cell_line="GM19238"

reads_count_chiapet_GM19238=featureCounts(
  read_bam_file(experiment, cell_line), 
  annot.ext = convert_peak_to_df_featcnt(peaks_with_motif_ChIAPET[[cell_line]]), 
  isPairedEnd = T, 
  nthreads = 100)

peaks_with_motif_ChIAPET[[cell_line]]$coverage=unname(reads_count_chiapet_GM19238$counts[,1])

cell_line="GM19239"

reads_count_chiapet_GM19239=featureCounts(
  read_bam_file(experiment, cell_line), 
  annot.ext = convert_peak_to_df_featcnt(peaks_with_motif_ChIAPET[[cell_line]]), 
  isPairedEnd = T, 
  nthreads = 100)

peaks_with_motif_ChIAPET[[cell_line]]$coverage=unname(reads_count_chiapet_GM19239$counts[,1])

cell_line="GM19240"

reads_count_chiapet_GM19240=featureCounts(
  read_bam_file(experiment, cell_line), 
  annot.ext = convert_peak_to_df_featcnt(peaks_with_motif_ChIAPET[[cell_line]]), 
  isPairedEnd = T, 
  nthreads = 100)

peaks_with_motif_ChIAPET[[cell_line]]$coverage=unname(reads_count_chiapet_GM19240$counts[,1])

####### HiChIP ######
experiment="hichip"

cell_line="GM19238"
reads_count_hichip_GM19238=featureCounts(
  read_bam_file(experiment, cell_line), 
  annot.ext = convert_peak_to_df_featcnt(peaks_with_motif_HiChIP[[cell_line]]), 
  isPairedEnd = T, 
  nthreads = 32)
peaks_with_motif_HiChIP[[cell_line]]$coverage=unname(reads_count_hichip_GM19238$counts[,1])

cell_line="GM19239"
reads_count_hichip_GM19239=featureCounts(
  read_bam_file(experiment, cell_line), 
  annot.ext = convert_peak_to_df_featcnt(peaks_with_motif_HiChIP[[cell_line]]), 
  isPairedEnd = T, 
  nthreads = 32)
peaks_with_motif_HiChIP[[cell_line]]$coverage=unname(reads_count_hichip_GM19239$counts[,1])

cell_line="GM19240"
reads_count_hichip_GM19240=featureCounts(
  read_bam_file(experiment, cell_line), 
  annot.ext = convert_peak_to_df_featcnt(peaks_with_motif_HiChIP[[cell_line]]), 
  isPairedEnd = T, 
  nthreads = 32)
peaks_with_motif_HiChIP[[cell_line]]$coverage=unname(reads_count_hichip_GM19240$counts[,1])

####### ChIP-Seq ######
experiment="chipseq"

cell_line="GM19238"
reads_count_chipseq_GM19238=featureCounts(
  read_bam_file(experiment, cell_line), 
  annot.ext = convert_peak_to_df_featcnt(peaks_all_with_motif_ChIPSeq[[cell_line]]), 
  isPairedEnd = T, 
  nthreads = 32)
peaks_all_with_motif_ChIPSeq[[cell_line]]$coverage=unname(reads_count_chipseq_GM19238$counts[,1])

cell_line="GM19239"
reads_count_chipseq_GM19239=featureCounts(
  read_bam_file(experiment, cell_line), 
  annot.ext = convert_peak_to_df_featcnt(peaks_all_with_motif_ChIPSeq[[cell_line]]), 
  isPairedEnd = T, 
  nthreads = 32)
peaks_all_with_motif_ChIPSeq[[cell_line]]$coverage=unname(reads_count_chipseq_GM19239$counts[,1])

cell_line="GM19240"
reads_count_chipseq_GM19240=featureCounts(
  read_bam_file(experiment, cell_line), 
  annot.ext = convert_peak_to_df_featcnt(peaks_all_with_motif_ChIPSeq[[cell_line]]), 
  isPairedEnd = T, 
  nthreads = 32)
peaks_all_with_motif_ChIPSeq[[cell_line]]$coverage=unname(reads_count_chipseq_GM19240$counts[,1])

## Or load them from the cluster, it will result in new peaks peaks_reduced_with_motif_coverage_(ChIAPET)
# load("coverage_chiapet", "coverage_hichip", "coverage_chipseq")

```

#Calculation of the TPM value
```{r}
trios<<-c("GM19238", "GM19239", "GM19240")
experiments=c("ChIAPET", "HiChIP", "ChIPSeq")
TPM_and_FPKM_values=vector(mode="list", length = NROW(trios))
names(TPM_and_FPKM_values)=trios

for (cell_line in trios){
  TPM_and_FPKM_values[[cell_line]]=vector(mode="list", length=NROW(experiments))
  names(TPM_and_FPKM_values[[cell_line]])=experiments
  
  tmp_tpm=c()
  for (experiment in experiments){
    TPM_and_FPKM_values[[cell_line]][[experiment]]=vector(mode="list", NROW(GM19238_common_peaks_3_tech_red))
    names(TPM_and_FPKM_values[[cell_line]][[experiment]])=names(GM19238_common_peaks_3_tech_red)
    
    for (overlap in names(GM19238_common_peaks_3_tech_red)){
      TPM_and_FPKM_values[[cell_line]][[experiment]][[overlap]]=
        calculate_FPKM_TPM(subsetByOverlaps(get(paste0("peaks_with_motif_coverage_", experiment))[[cell_line]], 
                                            get(paste0(cell_line, "_common_peaks_3_tech_red"))[[overlap]]))
    }
  }
}
rm(tmp_tpm)

```

# Create the violin plots of TPM value
```{r}
trios<<-c("GM19238", "GM19239", "GM19240")
experiments=c("ChIAPET", "HiChIP", "ChIPSeq")
# Orders of overlaps from from names(ctcf_strength_GM19238)
ord_of_overlaps=c(5,2,6,7,3,4,1)

# final Boxplots names
names_box_plot_tpm <- c(paste("\nCommon \npeaks\n for 3 technologies"), 
                    paste("\nCommon \npeaks\nChIA-PET & \nHi-ChIP"), 
                    paste("\nCommon \npeaks\n ChIP-Seq & \nChIA-PET"), 
                    paste("\nCommon \npeaks\n ChIP-Seq & \nHi-ChIP"), 
                    paste("\nUnique \npeaks\n ChIA-PET"), 
                    paste("\nUnique \npeaks\n Hi-ChIP"), 
                    paste("\nUnique \npeaks\n ChIP-Seq")) 

colors=c("#d36f4f","#73cb91", "#db4e97","#ed8f48", "#9496ff","#b1fe88", "#ff8f92")

for (cell_line in trios){
  for (experiment in experiments){
    png(paste0("plots/peaks/TPM_value_", cell_line,"_",experiment,"_box_plot.png"), res = 300, width = 5000, height = 3000)
    plot.new()
    tpm_value=data.frame()
    
    for (overlap in names(TPM_and_FPKM_values$GM19238$ChIAPET)[ord_of_overlaps]){
      if(length(TPM_and_FPKM_values[[cell_line]][[experiment]][[overlap]]$TPM)==0){
        tmp_value_df=data.frame(value=0, variable=overlap)
        tpm_value=rbind(tpm_value,tmp_value_df)
        }
      else{
        tmp_value_df=data.frame(value = TPM_and_FPKM_values[[cell_line]][[experiment]][[overlap]]$TPM, 
                              variable = overlap)
        tpm_value=rbind(tpm_value,tmp_value_df)
      }
    }
    
    rm(tmp_value_df)
    tpm_value=tpm_value%>%
      mutate(variable=factor(variable,levels=names(TPM_and_FPKM_values$GM19238$ChIAPET)[ord_of_overlaps]))
    
    print(
      ggplot(tpm_value, aes(x=variable, y=value, fill=variable))+  
        geom_boxplot(width=0.1)+
        theme_minimal()+
        scale_x_discrete(labels=names_box_plot_tpm[ord_of_overlaps])+
        theme(text = element_text(size=25),
              axis.text.x = element_text(angle=0, hjust=0.5))+
        scale_fill_manual(values=colors[ord_of_overlaps])+
        theme(legend.position="none")+
        ylab("TPM value")+
        xlab(c())+
        ylim(0,5000))
    dev.off()
  }

}


```

# Transposed: In order to make the same scale for the groups of the experiments, they will be compared only inside of the groups
```{r}

trios<<-c("GM19238", "GM19239", "GM19240")
experiments=c("ChIAPET", "HiChIP", "ChIPSeq")
# Orders of overlaps from from names(ctcf_strength_GM19238)
ord_of_overlaps=c(5,2,6,7,3,4,1)
colors=c("#d36f4f","#73cb91", "#db4e97","#ed8f48", "#9496ff","#b1fe88", "#ff8f92")

for (cell_line in trios){
  for (overlap in names(TPM_and_FPKM_values$GM19238$ChIAPET)[ord_of_overlaps]){
    png(paste0("plots/peaks/TPM_value_", cell_line,"_",overlap,"_lim_violin.png"), res = 300, width = 3000, height = 1000)
    plot.new()
    tpm_value=data.frame()
    
    for (experiment in experiments){
      if(length(TPM_and_FPKM_values[[cell_line]][[experiment]][[overlap]]$TPM)==0){
        tmp_value_df=data.frame(value=0, variable=experiment)
        tpm_value=rbind(tpm_value,tmp_value_df)
        }
      else{
        tmp_value_df=data.frame(value = TPM_and_FPKM_values[[cell_line]][[experiment]][[overlap]]$TPM, 
                              variable = experiment)
        tpm_value=rbind(tpm_value,tmp_value_df)
      }
    }
    if (overlap=="unique_ChIAPET" | overlap=="unique_HiChIP") {set_y_lim=2000}
    else if(overlap=="unique_ChIPSeq") {set_y_lim=600}
    else if (overlap=="common_ChIAPET_ChIPSeq" | overlap=="common_HiChIP_ChIPSeq") {set_y_lim=800}
    else if (overlap=="common_ChIAPET_HiChIP") {set_y_lim=10000}
    else {set_y_lim=200}
    
    rm(tmp_value_df)
    tpm_value=tpm_value%>%mutate(variable=factor(variable,levels=experiments))
     
    print(
      ggplot(tpm_value, aes(x=variable, y=value, fill=variable))+  
        geom_violin()+
        geom_boxplot(width=0.1)+
        theme_minimal()+
        scale_x_discrete(labels=c("ChIA-PET", "HiChIP", "ChIP-Seq"))+
        theme(text = element_text(size=25),
              axis.text.x = element_text(angle=0, hjust=0.5))+
        scale_fill_manual(values=rep(colors[which(names(TPM_and_FPKM_values$GM19238$ChIAPET)==overlap)],3))+
        theme(legend.position="none")+
        ylab("TPM value")+
        xlab(c())+
        ylim(0,set_y_lim)
      )
    dev.off()
    }
}

```

# Make violin plots that are only nessesary
```{r}
trios<<-c("GM19238")
experiments=c("ChIAPET", "HiChIP", "ChIPSeq")
# Orders of overlaps from from names(ctcf_strength_GM19238)
ord_of_overlaps=c(5,2,6,7,3,4,1)
colors=c("#d36f4f","#73cb91", "#db4e97","#ed8f48", "#9496ff","#b1fe88", "#ff8f92")

for (cell_line in trios){
  for (overlap in names(TPM_and_FPKM_values$GM19238$ChIAPET)[ord_of_overlaps]){
    if (overlap=="unique_ChIAPET"){
      which_labels=1
      w=1200}
    if (overlap=="common_ChIAPET_HiChIP"){
      which_labels=c(1:2)
      w=2200}
    if (overlap=="unique_HiChIP"){
      which_labels=2
      w=1200}
    if (overlap=="unique_ChIPSeq"){
      which_labels=3
      w=1200}
    if (overlap=="common_ChIAPET_ChIPSeq"){
      which_labels=c(1,3)
      w=2200}
    if (overlap=="common_HiChIP_ChIPSeq"){
      which_labels=c(2:3)
      w=2200}
    if (overlap=="constant_peaks"){
      which_labels=c(1:3)
      w=3000}
    
    png(paste0("plots/peaks/TPM_value_", cell_line,"_",overlap,"_trial_lim_violin.png"), res = 300, width = w, height = 1000)
    plot.new()
    tpm_value=data.frame()
    
    for (experiment in experiments){
      if(length(TPM_and_FPKM_values[[cell_line]][[experiment]][[overlap]]$TPM)==0){
        }
      else{
        tmp_value_df=data.frame(value = TPM_and_FPKM_values[[cell_line]][[experiment]][[overlap]]$TPM, 
                              variable = experiment)
        tpm_value=rbind(tpm_value,tmp_value_df)
      }
    }
    if (overlap=="unique_ChIAPET" | overlap=="unique_HiChIP") {set_y_lim=2000}
    else if(overlap=="unique_ChIPSeq") {set_y_lim=600}
    else if (overlap=="common_ChIAPET_ChIPSeq" | overlap=="common_HiChIP_ChIPSeq") {set_y_lim=800}
    else if (overlap=="common_ChIAPET_HiChIP") {set_y_lim=10000}
    else {set_y_lim=200}
    
    rm(tmp_value_df)
    tpm_value=tpm_value%>%mutate(variable=factor(variable,levels=experiments))
     
    print(
      ggplot(tpm_value, aes(x=variable, y=value, fill=variable))+  
        geom_violin()+
        geom_boxplot(width=0.1)+
        theme_minimal()+
        scale_x_discrete(labels=c("ChIA-PET", "HiChIP", "ChIP-Seq")[which_labels])+
        theme(text = element_text(size=25),
              axis.text.x = element_text(angle=0, hjust=0.5))+
        scale_fill_manual(values=rep(colors[which(names(TPM_and_FPKM_values$GM19238$ChIAPET)==overlap)],3))+
        theme(legend.position="none")+
        ylab("TPM value")+
        xlab(c())+
        ylim(0,set_y_lim)
      )
    dev.off()
    }
}

```

# Comparison between the trios on the same technology (x3)
```{r}
trios<<-c("GM19238", "GM19239", "GM19240")
experiments<<-c("ChIAPET", "HiChIP", "ChIPSeq")

for (experiment in experiments){
  
  experiment_1<<-experiment_2<<-experiment_3<<-experiment
  
  common_peaks=find_true_all_relative_overlaps(get(paste0("peaks_wout_sex_chr_", experiment))$GM19238, 
                                            get(paste0("peaks_wout_sex_chr_", experiment))$GM19239, 
                                            get(paste0("peaks_wout_sex_chr_", experiment))$GM19240,
                                            "trios")
  assign(paste0("common_peaks_for_trios_", experiment), common_peaks)
  
  # Draw and save the plots
  png(paste0('plots/venn_diagrams/Common_peaks_inside_trios_', experiment, '.png'), res = 300, width = 4200, height = 4200)
  plot.new()
  draw_3_venn_diagram(common_peaks)
  dev.off()
}
rm(common_peaks)

```

# Comparison between the reduced trios on the same technology (x3))
```{r}
trios<<-c("GM19238", "GM19239", "GM19240")
experiments<<-c("ChIAPET", "HiChIP", "ChIPSeq")

for (experiment in experiments){
  
  experiment_1<<-experiment_2<<-experiment_3<<-experiment
  
  common_peaks=find_true_all_relative_overlaps(get(paste0("peaks_wout_sex_chr_reduced_", experiment))$GM19238, 
                                            get(paste0("peaks_wout_sex_chr_reduced_", experiment))$GM19239, 
                                            get(paste0("peaks_wout_sex_chr_reduced_", experiment))$GM19240,
                                            "trios")
  assign(paste0("common_reduced_peaks_for_trios_", experiment), common_peaks)
  
  # Draw and save the plots
  png(paste0('plots/venn_diagrams/Common_reduced_peaks_inside_trios_', experiment, '.png'), res = 300, width = 4200, height = 4200)
  plot.new()
  draw_3_venn_diagram(common_peaks)
  dev.off()
}
rm(common_peaks)

```

# Strength of CTCF motif for every technology (ChIA-PET, HiChIP and ChIP-Seq)
```{r}
experiments=c("ChIAPET","HiChIP","ChIPSeq")

#Create GRangesLists that will conclude peaks with CTCF strength info

for (experiment in experiments){
  
  ctcf_strength=GRangesList(GRanges(),GRanges(),GRanges(),GRanges(),GRanges(),GRanges(),GRanges())
  names(ctcf_strength)=names(common_reduced_peaks_for_trios_ChIAPET)
  
  for (overlap in names(ctcf_strength)){
  
    ctcf_strength[[overlap]]=add_motif_info_to_peaks(get(paste0("common_reduced_peaks_for_trios_", experiment))[[overlap]], CTCF.hg38)
    assign(paste0("ctcf_strength_", experiment), ctcf_strength)
  }
}
rm(ctcf_strength)

# Calculate the mean max CTCF motif strength
tmp=vector(mode="list", length=NROW(common_reduced_peaks_for_trios_ChIAPET))
names(tmp)=names(common_reduced_peaks_for_trios_ChIAPET)
avergae_max_ctcf_per_experiment=list(tmp,tmp,tmp)
names(avergae_max_ctcf_per_experiment)=experiments
rm(tmp)

for (experiment in experiments){
  for (overlap in names(common_reduced_peaks_for_trios_ChIAPET)){
    avergae_max_ctcf_per_experiment[[experiment]][[overlap]]=mean(get(paste0("ctcf_strength_", experiment))[[overlap]]$max_motif_CTCF)
  }
}

```

# Violin plots of CTCF motif inside of the experiment
```{r}
# Orders of overlaps from from names(ctcf_strength_ChIAPET)
ord_of_overlaps=c(1,3,4,2,5,6,7)

# final Violin plots names
names_box_plot <- c(paste("\nConstant \npeaks"), 
                    paste("\nCommon \npeaks\nmother & \nfather"), 
                    paste("\nCommon \npeaks\nmother & \ndaughter"), 
                    paste("\nCommon \npeaks\nfather & \ndaughter"), 
                    paste("\nUnique \npeaks\nmother"), 
                    paste("\nUnique \npeaks\nfather"), 
                    paste("\nUnique \npeaks\ndaughter")) 

colors=c("#bf7a94","#976ecf", "#ff5952","#9cae8c", color("GM19238"),color("GM19239"), color("GM19240"))

for (experiment in experiments){
  png(paste0("plots/peaks/CTCF_motif_strength_", experiment,"_violin.png"), res = 300, width = 4000, height = 1500)
  plot.new()
  
  ctcf_strength_max_motif=data.frame()
  for (overlap in names(ctcf_strength_ChIAPET)[ord_of_overlaps]){
    tmp_ctcf_df=data.frame(value=get(paste0("ctcf_strength_", experiment))[[overlap]]$max_motif_CTCF, variable=overlap)
    ctcf_strength_max_motif=rbind(ctcf_strength_max_motif,tmp_ctcf_df)
  }
  rm(tmp_ctcf_df)
  ctcf_strength_max_motif=ctcf_strength_max_motif%>%
    mutate(variable=factor(variable,levels=names(get(paste0("ctcf_strength_", experiment)))[ord_of_overlaps]))
  
  print(ggplot(ctcf_strength_max_motif, aes(x=variable, y=value, fill=variable))+  
  geom_violin()+
  geom_boxplot(width=0.1)+
  theme_minimal()+
  # scale_x_discrete(labels=names_box_plot[ord_of_overlaps])+
  theme(text = element_text(size=25),
        axis.text.x = element_text(angle=0, hjust=0.5))+
  scale_fill_manual(values=colors[ord_of_overlaps])+
  theme(legend.position="none")+
  ylab("CTCF motif score")+
  xlab(c()))
  
  dev.off()
  
}

```

# Compare if subsets of peaks between technologies are the same | overlap of overlaps
```{r}

# Find how many peaks are common for the same regions in different technologies
overlaps_of_overlaps=list(constant_peaks=data.frame(), 
                          common_38_40=data.frame(), common_39_40=data.frame(),common_38_39=data.frame(),
                          unique_38=data.frame(), unique_39=data.frame(), unique_40=data.frame())

for (com_groups in names(overlaps_of_overlaps)){
  overlaps_of_overlaps[[com_groups]]=
    get_percentg_common_peaks(
    find_true_all_relative_overlaps(common_reduced_peaks_for_trios_ChIAPET[[com_groups]],
                                    common_reduced_peaks_for_trios_HiChIP[[com_groups]],
                                    common_reduced_peaks_for_trios_ChIPSeq[[com_groups]],
                                    "experiments"))
}

```

# Strength of CTCF motif for overlap of overlaps
```{r}
# Calculate the mean max CTCF motif strength
max_ctcf_of_overlaps_of_overlaps=vector(mode="list", length=NROW(names(overlaps_of_overlaps)))
names(max_ctcf_of_overlaps_of_overlaps)=names(overlaps_of_overlaps)


for (com_groups in names(max_ctcf_of_overlaps_of_overlaps)){
  tmp_const=find_true_all_relative_overlaps(common_reduced_peaks_for_trios_ChIAPET[[com_groups]],
                                    common_reduced_peaks_for_trios_HiChIP[[com_groups]],
                                    common_reduced_peaks_for_trios_ChIPSeq[[com_groups]],
                                    "experiments")
  max_ctcf_of_overlaps_of_overlaps[[com_groups]]=data.frame(matrix(NA, nrow=NROW(names(tmp_const))))
  row.names(max_ctcf_of_overlaps_of_overlaps[[com_groups]])=names(tmp_const[c(1,3,4,2,5,6,7)])
  
  tmp_ctcf=c()
  
  for (overlap in names(tmp_const[c(1,3,4,2,5,6,7)])){
    tmp_const[[overlap]]=add_motif_info_to_peaks(tmp_const[[overlap]], CTCF.hg38)
    tmp_ctcf=c(tmp_ctcf,mean(tmp_const[[overlap]]$max_motif_CTCF))
  }
  
  max_ctcf_of_overlaps_of_overlaps[[com_groups]]$ctcf_strength=tmp_ctcf
}
rm(tmp_const, tmp_ctcf)

```

# Violin plots of CTCF motif
```{r}
# Orders of overlaps from from names(ctcf_strength_GM19238)
ord_of_overlaps=c(5,2,6,7,3,4,1)

# final Boxplots names
names_box_plot <- c(paste("\nCommon \npeaks\n for 3 technologies"), 
                    paste("\nCommon \npeaks\nChIA-PET & \nHiChIP"), 
                    paste("\nCommon \npeaks\n ChIP-Seq & \nChIA-PET"), 
                    paste("\nCommon \npeaks\n ChIP-Seq & \nHiChIP"), 
                    paste("\nUnique \npeaks\n ChIA-PET"), 
                    paste("\nUnique \npeaks\n HiChIP"), 
                    paste("\nUnique \npeaks\n ChIP-Seq")) 

colors=c("#d36f4f","#73cb91", "#db4e97","#ed8f48", "#9496ff","#b1fe88", "#ff8f92")

for (cell_line in trios){
  png(paste0("plots/peaks/CTCF_motif_strength_", cell_line,"_violin.png"), res = 300, width = 5000, height = 3000)
  plot.new()
  
  ctcf_strength_max_motif=data.frame()
  for (overlap in names(ctcf_strength_GM19238)[ord_of_overlaps]){
    tmp_ctcf_df=data.frame(value=get(paste0("ctcf_strength_", cell_line))[[overlap]]$max_motif_CTCF, variable=overlap)
    ctcf_strength_max_motif=rbind(ctcf_strength_max_motif,tmp_ctcf_df)
  }
  rm(tmp_ctcf_df)
  ctcf_strength_max_motif=ctcf_strength_max_motif%>%
    mutate(variable=factor(variable,levels=names(get(paste0("ctcf_strength_", cell_line)))[ord_of_overlaps]))
  
  print(ggplot(ctcf_strength_max_motif, aes(x=variable, y=value, fill=variable))+  
  geom_violin()+
  geom_boxplot(width=0.1)+
  theme_minimal()+
  scale_x_discrete(labels=names_box_plot[ord_of_overlaps])+
  theme(text = element_text(size=25),
        axis.text.x = element_text(angle=0, hjust=0.5))+
  scale_fill_manual(values=colors[ord_of_overlaps])+
  theme(legend.position="none")+
  ylab("Strongest CTCF motif score")+
  xlab(c()))
  
  dev.off()
}

```








